---
title: "EE vs ENE Models: Model 6"
date: "`r Sys.Date()`"

format: 
  docx:
    reference-doc: "D:/PATHWEIGH/custom-reference-doc.docx"
    toc: true

execute: 
  echo: false
---

```{r}
# ee vs ene data to answer aim 1
```

```{r, warning=FALSE, message=FALSE}
invisible(library(tidyverse))
library(gtsummary)
library(magrittr, include.only = "%<>%")
```

```{r, plot_obs_vs_pred function}
# Function to plot observed vs fitted values

plot_obs_vs_pred <- function(mod) {
# Plot the observed and predicted values
obs_pred <- bind_cols(
  data,
  tibble(predicted = predict(mod, data, type = "response"))
  ) %>%
  mutate(
    observed = Weight_dv
  ) %>%
  select(
    Arb_PersonId, 
    N_months_post_id, 
    observed, 
    predicted, 
    Intervention.factor, 
    Cohort, 
    GroupID
  )

# convert to long
obs_pred_long <- obs_pred %>%
  group_by(
    Arb_PersonId, 
    N_months_post_id
  ) %>%
  pivot_longer(
    cols = c(observed, predicted), 
    values_to = "Weight", 
    names_to = "Type"
  ) %>%
  ungroup()

# display plot
obs_pred_long %>%
  group_by(N_months_post_id, Type) %>% # We could make the average profile and make 18 months 
  summarise(
    avg_weight_kgs = mean(Weight), 
    .groups = "drop"
  ) %>%
  filter(N_months_post_id <= 48) %>%
  ggplot(
    aes(x = N_months_post_id, y = avg_weight_kgs, color = Type)
  ) +
  geom_point() +
  geom_line() + 
  theme(legend.position="bottom")
}
```

```{r}
# Plot the pridected and residual values
plot_res_vs_pred <- function(mod) {

  # Extract fitted values and residuals
  # Considers the random effects
  fitted_vals <- fitted(mod)
  residuals <- residuals(mod)

  # Basic diagnostic plot
  plot(fitted_vals, residuals,
      xlab = "Fitted values",
      ylab = "Residuals",
      main = "Residuals vs Fitted")
  abline(h = 0, col = "red")
}
```


```{r}  
# Set the project root
proj_root <- "D:/PATHWEIGH/"

# Set the data delivery date to the appropriate data set
delivery <- "20240917"

# Load pp_data for ensuring that the same 9,358 patients are analyzed
load(
  str_c(
    proj_root, 
    "delivery_", delivery, 
    "/data/pp_data_", delivery, 
    ".Rdata"
  )
)

# Load visits_post_id to create merge in variables
load(
  str_c(
    proj_root, 
    "delivery_", delivery, 
    "/data/visits_post_id_", delivery, 
    ".Rdata"
  )
)
```

```{r, message = FALSE, warning = FALSE}
# Load data
data <- read_csv(
  "D:\\PATHWEIGH\\delivery_20240917\\data\\aim3_its_data_20240917.csv"
)
```

```{r}
# Convert days to months
data %<>% 
  mutate(
    N_months_post_id_con = N_days_post_id / 30,
    N_months_post_id_int = N_days_post_int / 30,
    N_months_post_wpv_con = N_days_post_wpv / 30,
    N_months_post_wpv_int = N_days_post_wpv_int / 30,
    N_months_post_pw = N_days_post_pw / 30
  ) %>% 
  # Needed for plotting obs vs predicted correctly
  mutate(N_months_post_id = floor(N_months_post_id_con))
```

```{r}
# Create varaibles
data %<>%
  mutate(
    N_months_post_id_con_180 = N_months_post_id_con,
    N_months_post_id_con_570 = N_months_post_id_con,
    N_months_post_id_int_180 = N_months_post_id_int,
    N_months_post_wpv_con_180 = N_months_post_wpv_con,
    N_months_post_wpv_int_180 = N_months_post_wpv_int,
    N_months_post_pw_180 = N_months_post_pw
  ) %>%
  mutate(
    N_months_post_id_con_180 = ifelse(N_months_post_id_con <= 6, 0, N_months_post_id_con_180 - 6),
    N_months_post_id_con_570 = ifelse(N_months_post_id_con <= 19, 0, N_months_post_id_con_570 - 19),
    N_months_post_id_int_180 = ifelse(N_months_post_id_int_180 <= 6, 0, N_months_post_id_int_180 - 6),
    N_months_post_wpv_con_180 = ifelse(N_months_post_wpv_con_180 <= 6, 0, N_months_post_wpv_con_180 - 6),
    N_months_post_wpv_int_180 =ifelse(N_months_post_wpv_int_180 <= 6, 0, N_months_post_wpv_int_180 - 6),
    N_months_post_pw_180 = ifelse(N_months_post_pw_180 <= 6, 0, N_months_post_pw_180  - 6)
  )


```


```{r}
data %<>%
  mutate(
    year0 = ifelse(Year == "Year0", 1, 0),
    year1 = ifelse(Year == "Year1", 1, 0),
    year2 = ifelse(Year == "Year2", 1, 0),
    year3 = ifelse(Year == "Year3", 1, 0),
    year4 = ifelse(Year == "Year4", 1, 0)
  )
```

```{r}
# Set parameters for digits
n_digits = 5
```

## Model 6
Mixed effects linear regression model with random patient and clinic random/fixed effects including linear function for N_days_post_id, N_days_post_int
```{r, eval = TRUE, echo = TRUE}
model_6 <- lmerTest::lmer(
  Weight_dv ~
    # age
    age_45_to_60 + age_gt_60 +

    # sex
    sex_m +

    # race ethnicity
    reth_his + reth_blk + reth_asn + reth_oth + reth_ukn +

    # Year at the index visit (first visit with a weight)
    year_at_ind1 + year_at_ind2 + year_at_ind3 +
      
    # Time variables
    N_months_post_id_con + N_months_post_id_con_180 + N_months_post_id_con_570 +

    N_months_post_id_int + N_months_post_id_int_180 + 
      
    N_months_post_wpv_con + N_months_post_wpv_con_180 + 
      
    N_months_post_wpv_int + N_months_post_wpv_int_180 +

    N_months_post_pw +


    (1| Arb_PersonId) + (1|DepartmentExternalName),

  data = data)
```

```{r, eval = TRUE}
tbl_regression(model_6, intercept = TRUE, 
               estimate_fun = purrr::partial(style_ratio, digits = n_digits)) %>%
  add_glance_table(include = c("nobs", "sigma", "logLik", "AIC", "BIC", "REMLcrit", "df.residual")) %>%
  as_gt() #%>%
  # gt::gtsave(., filename = "D:/PATHWEIGH/delivery_20240917/scripts/ee_vs_ene/ee_vs_ene_models/model_6.docx" )
```


## Residual vs predicted/fitted values
- Predicted/fitted values consider random effects
```{r}
plot_res_vs_pred(model_6) 
```

## QQ Plot

```{r}
# Extract residuals
res <- resid(model_6)

# Base R QQ plot
qqnorm(res)
qqline(res, col = "red")
```


## Observed vs predicted values
- Considers the random effects in predictions
- Individual values averaged within each month
```{r}
# Plot observed vs fitted values
plot_obs_vs_pred(model_6)
```

```{r}
# Create a data set for plotting
obs_pred <- bind_cols(
  data,
  tibble(predicted = predict(model_6, data, type = "response"))
  ) %>%
  mutate(
    observed = Weight_dv
  )
```


```{r}
# Calculate the n_visits_per_pt per phase
n_visits_per_pt <- 
  data %>%
  group_by(Arb_PersonId, Intervention.factor) %>%
  count() %>%
  ungroup() %>%
  pivot_wider(names_from = Intervention.factor, values_from = n) %>%
  mutate(across(Control:Intervention, ~ifelse(is.na(.x), 0, .x)))
```


<!-- FUNCTION TO PLOT DIAGNOSTIC PLOTS -->
```{r}
# Function to plot obs vs predicted in separate subgroups
plot_obs_pred_v2 <-  function(data) {
  data %>%
  select(
    Arb_PersonId, 
    N_months_post_id, 
    observed, 
    predicted, 
    Intervention.factor, 
    EE, 
    GroupID
  ) %>%
  group_by(
    Arb_PersonId, 
    N_months_post_id
  ) %>%
  pivot_longer(
    cols = c(observed, predicted), 
    values_to = "Weight", 
    names_to = "Type"
  ) %>%
  ungroup() %>%
  group_by(
    N_months_post_id, 
    Type, 
    EE
  ) %>%
  summarise(
    avg_weight_kgs = mean(Weight),
    .groups = "drop"
  ) %>%
  filter(N_months_post_id <= 48 ) %>%
  ggplot(
    aes(x = N_months_post_id, y = avg_weight_kgs, color = Type)
  ) +
  geom_point() +
  geom_line() +
  facet_wrap( ~ EE) +
  theme(legend.position="bottom")
}
```


## Plot of observed vs predicted after averaging by month for those with visits in control only
- 0 = ENE
- 1 = EE
```{r}
obs_pred %>%
  filter(
    Arb_PersonId %in% (n_visits_per_pt %>% filter(Control > 0, Intervention == 0) %>% pull(Arb_PersonId))
  ) %>%
  plot_obs_pred_v2()
```

## Plot of observed vs predicted after averaging by month for those with visits in intervention only
- 0 = ENE
- 1 = EE
```{r}
obs_pred %>%
  filter(
    Arb_PersonId %in% (n_visits_per_pt %>% filter(Control == 0, Intervention > 0) %>% pull(Arb_PersonId))
  ) %>%
  plot_obs_pred_v2()
```

## Plot of observed vs predicted after averaging by month for those with 1 visits in control and  1 visit in intervention
- 0 = ENE
- 1 = EE
* All of these individuals have N_months_post_id value equal to 0, because the have 1 and only 1 visit after their index
```{r}
obs_pred %>%
  filter(
    Arb_PersonId %in% (n_visits_per_pt %>% filter(Control == 1, Intervention == 1) %>% pull(Arb_PersonId))
  ) %>% #pull(N_months_post_id) %>% table()
  # select(N_months_post_id, N_months_post_id_con)
  plot_obs_pred_v2()
```


## Plot of observed vs predicted after averaging by month for those with 2 or more visits in control and only 1 visit in intervention
- 0 = ENE
- 1 = EE
```{r}
obs_pred %>%
  filter(
    Arb_PersonId %in% (n_visits_per_pt %>% filter(Control >= 2, Intervention == 1) %>% pull(Arb_PersonId))
  ) %>%
  plot_obs_pred_v2()
```


## Plot of observed vs predicted after averaging by month for those with 2 or more visits in intervention and only 1 visit in control
- 0 = ENE
- 1 = EE
```{r}
obs_pred %>%
  filter(
    Arb_PersonId %in% (n_visits_per_pt %>% filter(Control == 1, Intervention >= 2) %>% pull(Arb_PersonId))
  ) %>%
  plot_obs_pred_v2()
```

## Plot of observed vs predicted after averaging by month for those with 2 or more visits in intervention and 2 or more visit in control
- 0 = ENE
- 1 = EE
```{r}
obs_pred %>%
  filter(
    Arb_PersonId %in% (n_visits_per_pt %>% filter(Control >= 2, Intervention >= 2) %>% pull(Arb_PersonId))
  ) %>%
  plot_obs_pred_v2()
```