---
title: "EE vs ENE Patient Flow Diagram"
date: "`r Sys.Date()`"

format: 
  docx:
    reference-doc: "D:/PATHWEIGH/custom-reference-doc.docx"
    toc: true

execute: 
  echo: false
---

```{r}
# ee vs ene data to answer aim 1
```

```{r, warning=FALSE, message=FALSE}
invisible(library(tidyverse))
library(gtsummary)
library(magrittr, include.only = "%<>%")

# Loads the common set of functions for data deliveries 03-22-2023 and beyond
source(str_c(emr_dir, "subscripts/source_subscripts.R"))
```

## Total number of encounters delivered

```{r}
# Current participant flow diagram starts with total unique number of encounters delivered
# not the number of encounters from 18+ and BMI > 25
read_pw_csv("encounter")
```

```{r}
encounter %>%
    distinct(Arb_EncounterId) %>%
    nrow()
```

## Total number of patients
```{r}
encounter %>%
    distinct(Arb_PersonId) %>%
    nrow()
```

## Total number of eligible patients 18+, BMI >= 25, and two or more visits with a recorded weight
```{r}
# Number of eligible patients
data <- read_csv("D:\\PATHWEIGH\\delivery_20240917\\data\\aim3_its_data_20240917.csv")
```

```{r}
# Fix the EE column
ee_pts <- 
    data %>%
    filter(WP_Visit == 1) %>%
    distinct(Arb_PersonId)

data <- 
    data %>%
    mutate(EE = ifelse(Arb_PersonId %in% ee_pts$Arb_PersonId, 1, 0))
```



```{r}
data %>%
    select(Arb_PersonId) %>%
    distinct() %>%
    nrow()
```

```{r}
#| eval: false
# Check that each patient has 2 or more visits

data %>% 
    group_by(Arb_PersonId) %>%
    count() %>%
    ungroup() %>%
    filter(n < 2) %>%
    nrow()
```

## Total number of patients that received care for their weight (WPV)
- had at least one wpv at any time during the study period, regardless of what phase it was in

```{r}
n_wpv_visits <- 
    data %>% 
    filter(WP_Visit == 1) %>%
    group_by(Arb_PersonId, Intervention.factor) %>%
    count() %>%
    ungroup() %>%
    pivot_wider(names_from = Intervention.factor, values_from = n) %>%
    mutate(across(Control:Intervention, ~ifelse(is.na(.x), 0, .x)))
```

```{r}
n_wpv_visits %>%
    select(Arb_PersonId) %>%
    distinct() %>%
    nrow()
```

### Total number of patients who received care for their weight in control only
```{r}
n_wpv_visits %>%
    filter(Control > 0, Intervention == 0) %>%
    nrow()
```


### Total number of patients who received care for their weight in intervention only
```{r}
n_wpv_visits %>%
    filter(Control == 0, Intervention > 0) %>%
    nrow()
```

### Total number of patients who received care for their weight in both phases

```{r}
n_wpv_visits %>%
    filter(Control > 0, Intervention > 0) %>%
    nrow()
```

## Number of patients that have visits across multiple clinics
```{r}
# How many patients have visits in multiple clinics
data %>%
    group_by(Arb_PersonId) %>%
    summarise(distinct_groups = n_distinct(GroupID)) %>%
    filter(distinct_groups > 1) %>%
    nrow()
```

# Number of patients in each cohort
```{r}
data %>%
    filter(EE == 1) %>%
    group_by(Arb_PersonId) %>%
    slice_head() %>%
    ungroup() %>%
    select(Cohort) %>%
    tbl_summary()


data %>%
    filter(WP_Visit == 1) %>%
    group_by(Arb_PersonId) %>%
    slice_head() %>%
    ungroup() %>%
    select(Cohort) %>%
    tbl_summary()


data %>%
    filter(WP_Visit == 1) %>%
    pull(EE) %>%
    table()


data %>%
    filter(EE == 1) %>%
    pull(WP_Visit) %>%
    table()
```


```{r}
data %>%
    filter(EE == 1) %>%
    select(Arb_PersonId) %>%
    distinct() %>%
    nrow()
```


```{r}
pt_ids_w_wpv <- 
    data %>%
    filter(WP_Visit == 1) %>%
    select(Arb_PersonId) %>%
    distinct()
```


```{r}
pt_ids_w_ee <- 
    data %>%
    filter(EE == 1) %>%
    select(Arb_PersonId) %>%
    distinct()
```


```{r}
ids_to_check <- anti_join(pt_ids_w_ee, pt_ids_w_wpv)
```


```{r}
inspect_df <- data %>%
    filter(Arb_PersonId %in% ids_to_check$Arb_PersonId) %>%
    select(Arb_PersonId, Arb_EncounterId, EncounterDate, EE, WP_Visit, Intervention.factor)
```