---
title: "EE vs ENE Patient Flow Diagram"
date: "`r Sys.Date()`"

format: 
  docx:
    reference-doc: "D:/PATHWEIGH/custom-reference-doc.docx"
    toc: true

execute: 
  echo: false
---

```{r}
# ee vs ene data to answer aim 1
```

```{r, warning=FALSE, message=FALSE}
invisible(library(tidyverse))
library(gtsummary)
library(magrittr, include.only = "%<>%")
library(here)
```

```{r}
# Needed to load read_pw_csv())
data_delivery_date <- 20240917

# Loads the common set of functions for data deliveries 03-22-2023 and beyond
# Needed to load the read_pw_csv() function
source("D:\\PATHWEIGH\\emr_data_processing\\functions\\read_pw_csv.R")
```

```{r}
# Set the path to the emr_data_processing directory to load scripts/functions
# that are shared along all separate data deliveries
proj_root_dir <- str_c("delivery_", data_delivery_date)
proj_parent_dir <- str_remove(here(), proj_root_dir)
emr_dir <- str_c(proj_parent_dir, "/emr_data_processing/")

# Current participant flow diagram starts with total unique number of encounters delivered
# not the number of encounters from 18+ and BMI > 25
read_pw_csv("encounter")
```

## Total number of encounters delivered

```{r}
encounter %>%
    distinct(Arb_EncounterId) %>%
    nrow()
```

## Total number of patients
```{r}
encounter %>%
    distinct(Arb_PersonId) %>%
    nrow()
```

## Total number of eligible patients
```{r}
load("D:\\PATHWEIGH\\delivery_20240917\\data\\all_visits_20240917.RData")
```
```{r}
# All eligible visits
visits %>%
  filter(Eligible == 1) %>%
  distinct(Arb_PersonId) %>%
  nrow()
```

## Total number of eligible patients 18+, BMI >= 25, and two or more visits with a recorded weight
```{r}
# Number of eligible patients
data <- read_csv("D:\\PATHWEIGH\\delivery_20240917\\data\\aim3_its_data_20240917.csv")
```

```{r}
# # Fix the EE column
# ee_pts <- 
#     data %>%
#     filter(WP_Visit == 1) %>%
#     distinct(Arb_PersonId)

# data <- 
#     data %>%
#     mutate(EE = ifelse(Arb_PersonId %in% ee_pts$Arb_PersonId, 1, 0))
```

```{r}
data %>%
    select(Arb_PersonId) %>%
    distinct() %>%
    nrow()
```

```{r}
#| eval: false
# Check that each patient has 2 or more visits

data %>% 
    group_by(Arb_PersonId) %>%
    count() %>%
    ungroup() %>%
    filter(n < 2) %>%
    nrow()
```

## Total number of patients by pattern of visits and cohort

```{r}
n_visits_per_pt <- 
    data %>% 
    group_by(Arb_PersonId, Intervention.factor) %>%
    count() %>%
    ungroup() %>%
    pivot_wider(names_from = Intervention.factor, values_from = n) %>%
    mutate(across(Control:Intervention, ~ifelse(is.na(.x), 0, .x)))

# Merge in the cohort
n_visits_per_pt <- n_visits_per_pt %>%
  left_join(
    (data %>%
      select(Arb_PersonId, Cohort) %>%
      distinct()),
    by = "Arb_PersonId")


visits_in_both <- 
  n_visits_per_pt %>%
    filter(Control > 0, Intervention > 0) %>%
    pull(Arb_PersonId)

visits_in_con <- 
  n_visits_per_pt %>%
    filter(Control > 0, Intervention == 0) %>%
    pull(Arb_PersonId)

visits_in_int <- 
  n_visits_per_pt %>%
    filter(Control == 0, Intervention > 0) %>%
    pull(Arb_PersonId)
```

### Cohort 1

```{r}
list(visits_in_con, visits_in_int, visits_in_both) %>%
  purrr::map( 
  ~ n_visits_per_pt %>%
    filter(Arb_PersonId %in% .x) %>%
    filter(Cohort == "Cohort1") %>%
    nrow()
  )
```

### Cohort 2

```{r}
list(visits_in_con, visits_in_int, visits_in_both) %>%
  purrr::map( 
  ~ n_visits_per_pt %>%
    filter(Arb_PersonId %in% .x) %>%
    filter(Cohort == "Cohort2") %>%
    nrow()
  )
```

### Cohort 3

```{r}
list(visits_in_con, visits_in_int, visits_in_both) %>%
  purrr::map( 
  ~ n_visits_per_pt %>%
    filter(Arb_PersonId %in% .x) %>%
    filter(Cohort == "Cohort3") %>%
    nrow()
  )
```


## Total number of patients that received care for their weight (WPV)
- had at least one wpv at any time during the study period, regardless of what phase it was in

```{r}
n_wpv_visits <- 
    data %>% 
    filter(WP_Visit == 1) %>%
    group_by(Arb_PersonId, Intervention.factor) %>%
    count() %>%
    ungroup() %>%
    pivot_wider(names_from = Intervention.factor, values_from = n) %>%
    mutate(across(Control:Intervention, ~ifelse(is.na(.x), 0, .x)))
```

```{r}
n_wpv_visits %>%
    select(Arb_PersonId) %>%
    distinct() %>%
    nrow()
```

### Total number of patients who received care for their weight in control only
```{r}
n_wpv_visits %>%
    filter(Control > 0, Intervention == 0) %>%
    nrow()
```


### Total number of patients who received care for their weight in intervention only
```{r}
n_wpv_visits %>%
    filter(Control == 0, Intervention > 0) %>%
    nrow()
```

### Total number of patients who received care for their weight in both phases

```{r}
n_wpv_visits %>%
    filter(Control > 0, Intervention > 0) %>%
    nrow()
```

## Number of patients that have visits across multiple clinics
```{r}
# How many patients have visits in multiple clinics
data %>%
    group_by(Arb_PersonId) %>%
    summarise(distinct_groups = n_distinct(GroupID)) %>%
    filter(distinct_groups > 1) %>%
    nrow()
```

# Number of patients in each cohort EE
```{r}
data %>%
    filter(EE == 1) %>%
    group_by(Arb_PersonId) %>%
    slice_head() %>%
    ungroup() %>%
    select(Cohort) %>%
    tbl_summary()
```

# Number of patients in each cohort ENE
```{r}
data %>%
  filter(EE == 0) %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup() %>%
  select(Cohort) %>%
  tbl_summary()
```

# Time spent in phase
```{r}
data %>%
  arrange(Arb_PersonId, Intervention, EncounterDate) %>%
  group_by(Arb_PersonId, Intervention) %>%
  slice_tail() %>%
  ungroup() %>%
  group_by(Intervention, EE) %>%
  select(N_months_post_id) %>%
  summarise(avg_t_in_phase = mean(N_months_post_id)) %>%
  arrange(EE)
```

# Patients with two or more visits in both phases and where at least one of the 2 visits or more visits is a WPV.
```{r}
# 9,358, use the actual data or the patients from a previous workflow are 
# different
ids_w_wpv_in_each_phase <- 
  n_wpv_visits %>%
  filter(Control > 0, Intervention > 0) %>%
  pull(Arb_PersonId)


n_visits_in_each_phase <- 
data %>% 
  filter(EE == 1) %>%
  group_by(Arb_PersonId, Intervention.factor) %>%
  count() %>%
  ungroup() %>%
  pivot_wider(names_from = Intervention.factor, values_from = n) %>%
  mutate(across(Control:Intervention, ~ifelse(is.na(.x), 0, .x)))
```

```{r}
n_visits_in_each_phase %>%
  filter(Arb_PersonId %in% ids_w_wpv_in_each_phase) %>%
  filter(Control >= 2 , Intervention >= 2) %>%
  distinct(Arb_PersonId) %>%
  nrow()
```


# Patients with at least one PW visit in the intervention
```{r}
data %>%
  filter(Intervention.factor == "Intervention") %>%
  filter(PW_Visit == 1) %>%
  select(starts_with("WPV_"), PW_Visit) %>%
  distinct() %>%
  nrow()
```


```{r}
table(data$Censored)
```


```{r}
data %>% 
  filter(Arb_PersonId %in% ee_ene)
```


```{r}
# Test to see how many of the pp data 9,358 patients are in the ee_ene_its_data
load("D:\\PATHWEIGH\\delivery_20240917\\data\\pp_data_20240917.RData")


# 9,345
data %>%
  filter(Arb_PersonId %in% pp_data$Arb_PersonId) %>%
  distinct(Arb_PersonId) %>%
  nrow()


```