---
title: "PP Tables & Figures"
format: 
  docx:
    reference-doc: "D:/PATHWEIGH/custom-reference-doc.docx"

params:
  delivery: "20240917"

execute: 
  echo: false
---

```{r, warning=FALSE, message=FALSE}
invisible(library(tidyverse))
library(gtsummary)
library(magrittr, include.only = "%<>%")
```

```{r, table formatting functions}
# Declare model output and table formatting functions

# Part 1
prep_mdl_out <- function(model_output) {
  # Set a vector for term labels of the binary variables that were not included in
  # the model because its not necessary to include sex_f and sex_m in the formula.
  # These terms are added for completeness when building the final output table
  # and are used to create an ordered vector of terms for displaying the table.
  term <- c("age_lt_45",
    "sex_f",
    "reth_nhw",
    "year_at_ind0")
  
  model_terms <- model_output %>% pull(term)
  
  # Set the order of the terms to organize them in a subsequent table
  ordered_terms <- c(
    model_terms[1],
    term[1],
    model_terms[2:3],
    term[2],
    model_terms[4],
    term[3],
    model_terms[5:9],
    term[4],
    model_terms[10:18]
  )
  
  # Create the main table
  # stack the vector terms with model_output
  tab <- 
    bind_rows(model_output,
              (data.frame(term) %>%
               mutate(effect = "fixed"))
              ) %>%
  
    # Arrange the terms in the previous step to the pre-specified orer
    arrange((factor(term, levels = ordered_terms))) %>%
  
    # remove columns that are not needed for display
    select(-effect, -statistic, -df) %>%
  
    # remove rows that are not needed for display
    # filter(!term %in% c("sd__(Intercept)", "sd__Observation")) %>%
  
    # convert the estimate for N_days_* to N_months_*
    mutate(estimate = ifelse(grepl("N_days_post", term), estimate * 30, estimate)) %>%
    mutate(std.error = ifelse(grepl("N_days_post", term), std.error * 30, std.error)) %>%
    mutate(conf.low = ifelse(grepl("N_days_post", term), conf.low * 30, conf.low)) %>%
    mutate(conf.high = ifelse(grepl("N_days_post", term), conf.high * 30, conf.high)) %>%
  
    # round values
    mutate(across(estimate:conf.high, ~round(., 3))) %>%
  
    # convert term N_days_* to N_months_* and slope* to human readable
    mutate(term = str_replace(term, "N_days_post_id", "N_months_post_id"),
           term = str_replace(term, "N_days_post_180", "N_months_post_180"),
           # term = str_replace(term, "slope1", "Control"),
           # term = str_replace(term, "slope2", "Intervention")
           ) %>%
  
    # relabel all of the values in the "term" column
    mutate(term = case_when(
      term == "age_lt_45" ~ "<45",
      term == "age_45_to_60" ~ "[45, 60)",
      term == "age_gt_60" ~ ">60",
      term == "sex_f" ~ "Female",
      term == "sex_m" ~ "Male",
      term == "reth_nhw" ~ "NonHispanicWhite",
      term == "reth_his" ~ "Hispanic",
      term == "reth_blk" ~ "Black",
      term == "reth_asn" ~ "Asian",
      term == "reth_oth" ~ "Other",
      term == "reth_ukn" ~ "Unknown",
      term == "year_at_ind0" ~ "0",
      term == "year_at_ind1" ~ "1",
      term == "year_at_ind2" ~ "2",
      term == "year_at_ind3" ~ "3",
      term == "Weight_bl" ~ "Weight_bl (kg)",
      .default = term))
    
  return(tab)
    
}

# Part 2
# Manually change slope terms

# Part 3
fmt_tab <- function(tab, title) {
  # Add grouping rows for the following terms
  tab %>%
  mutate(across(estimate:std.error, ~ as.character(.))) %>%
  mutate(across(p.value, ~sprintf("%.3f", .))) %>% # Converting to character, but preserve the trailing zeros
  gt::gt(rowname_col = "term") %>%
  gt::rows_add(
    term = "Age",
    estimate = "",
    std.error = "",
    p.value = "    ",
    .after = "(Intercept)"
  ) %>%
  gt::rows_add(
    term = "Gender",
    estimate = "",
    std.error = "",
    p.value = "",
    .before = "Female") %>%
  gt::rows_add(
    term = "Race/Ethnicity",
    estimate = "",
    std.error = "",
    p.value = "",
    .after = "Male") %>%
  gt::rows_add(
    term = "Year at Index",
    estimate = "",
    std.error = "",
    p.value = "",
    .before = "0") %>%
  gt::tab_header(
    title = title,
    # subtitle = "subtitle place holder"
  )
}
```

```{r}  
# Set the project root
proj_root <- "D:/PATHWEIGH/"

# Set the data delivery date to the appropriate data set
delivery <- params$delivery

# Load pp_data for creating tables
load(str_c(proj_root, "delivery_", delivery, "/data/pp_data_", delivery, ".Rdata"))

# Load visits_post_id
load(str_c(proj_root, "delivery_", delivery, "/data/processed_visits_post_id_", delivery, ".Rdata"))

# Load pp_mod_data for modeling
load(str_c(proj_root, "delivery_", delivery, "/data/pp_mod_data_", delivery, ".Rdata"))

# Save a copy as data so that it can be used as an input to other code chunks
data <- pp_data

# Load comorbidity names for tables
comorbidity_names <- readRDS(str_c(proj_root, "delivery_", delivery, "/data/comorbidity_names_", delivery, ".RDS"))
```

```{r}  
# Process visits_post_id for displaying tables
visits_post_id <- 
  visits_post_id %>%
  mutate(across(PHQ2:GAD7, ~ as.numeric(.)),
            EOSS = fct_na_value_to_level(factor(EOSS, levels = c("0", "1", "2", "3")), level = "Unknown"))

# NA the outlier with a BMI of 4.
visits_post_id %<>%
  mutate(BMI = ifelse(Arb_EncounterId == 170254415001, NA, BMI))
```

### The following output is automated. Some manual manipulation will be needed upon each iteration for the final manuscript
1. Change BMI kg/m^2 to superscript the 2.
2. Change font (once all tables/figs are finalized)

# Total sample
Data is restricted to those that had 2 or more visits in both control and intervention phases of the study from data delivery 2024-09-17.Enrollment cut off date of 2024-03-15.
```{r}
pp_mod_data %>%
  group_by(Arb_PersonId, Intervention) %>%
  slice_head() %>%
  ungroup() %>%
  select(Intervention) %>%
  tbl_summary(statistic = all_categorical() ~ "{n}") %>%
  # show_header_names()
  modify_header(stat_0 = "**Patients**") %>%
  as_gt()
```

# Table: Health metrics at index and last visits
```{r}
tab1 <- bind_rows(
(visits_post_id %>%
  filter(Arb_PersonId %in% data$Arb_PersonId, 
         IndexVisit == 1)),
(visits_post_id %>%
  filter(Arb_PersonId %in% data$Arb_PersonId, 
         LastVisit == 1))) %>%
  mutate(Visit = factor(ifelse(IndexVisit == 1, "Index Visit", "Final Visit"), levels = c("Index Visit", "Final Visit"))) %>%
  mutate(Intervention.factor = factor(Intervention.factor, levels = c("Control", "Intervention"))) %>%
  mutate(Smoking_Status = fct_na_value_to_level(Smoking_Status, level = "Unknown")) %>%
  select(Age, Weight_kgs, Sex, Race_Ethnicity, Insurance, BMI,
         Systolic_blood_pressure, Diastolic_blood_pressure,
         A1C:TSH, -`Cystatin C`, EOSS,
         PHQ2, PHQ9, GAD7, Smoking_Status,
         Intervention.factor, Visit) %>%
  tbl_strata(
    strata = "Intervention.factor",
    .tbl_fun = 
      ~ .x %>%
      tbl_summary(by = Visit,
                  missing = "ifany",
                  type = list(c(PHQ2, PHQ9, GAD7) ~ 'continuous'),
                  # statistic = list(all_continuous() ~ c("{mean} ({sd}; {min}; {max})")),
                  statistic = list(all_continuous() ~ c("{mean} ({sd})")),
                  label = list(Age ~ "Age (years)",
                               Weight_kgs ~ "Weight (kg)",
                               Race_Ethnicity ~ "Race/Ethnicity",
                               BMI ~ "BMI (kg/m^2)",
                               Systolic_blood_pressure ~ "Systolic BP (mmHg)",
                               Diastolic_blood_pressure ~ "Diastolic BP (mmHg)",
                               Smoking_Status ~ "Smoking Status"),
                  digits = list(all_categorical() ~ c(0,1),
                                  all_continuous() ~ c(1,1)))
        )

# Leigh wants to not display the sample size and instead state it in a caption
tab1 %<>%
  modify_header(stat_1_1 = "**Index Visit**",
                stat_2_1 = "**Final Visit**",
                stat_1_2 = "**Index Visit**",
                stat_2_2 = "**Final Visit**") %>%
  as_gt()

tab1
```

# Table: Identification of WPVs (OBHPI, WMQ, SMART, etc.) and referrals, procedures,
```{r}
# Table 3 WPVs ---------------------------------------------------------------
# Table 3 is created by merging two separate tables that are created in the
# same way, but have different  data sets. Sub table 3.1 consists of the index
# visits from those that are in mod_data[["ee"]] while sub table 3.2 consists
# of all visits in from analyzed patients found in visits_post_id including
# the index visits.

## Create data for sub table 3.1 ----
# Capture index visits for those in control phase in mod data
wpv_con_ind <- visits_post_id %>%
  filter(Arb_PersonId %in% (data %>% filter(Intervention == "Control") %>% distinct(Arb_PersonId) %>% pull(Arb_PersonId))) %>%
  filter(Intervention.factor == "Control",
         IndexVisit == 1)

# Capture index visits for those in intervention phase in mod data
wpv_int_ind <- visits_post_id %>%
  filter(Arb_PersonId %in% (data %>% filter(Intervention == "Intervention") %>% distinct(Arb_PersonId) %>% pull(Arb_PersonId))) %>%
  filter(Intervention.factor == "Intervention",
         IndexVisit == 1)

## Create wpv_data by stacking index visits in control and in intervention ----
# wpv_data <- bind_rows(wpv_con_ind, wpv_int_ind)

# Commented out because there is no need for pp_data to list analyzed and full
## Create data for sub table 3.2 ----
# WPVs from all of those in mod_data, including the Index Visit
# Capture index visits for those in control phase in mod data
wpv_con_an_all <- visits_post_id %>%
  filter(Arb_PersonId %in% (data %>% filter(Intervention == "Control") %>% distinct(Arb_PersonId) %>% pull(Arb_PersonId))) %>%
  filter(Intervention.factor == "Control")

# Capture index visits for those in intervention phase in mod data
wpv_int_an_all <- visits_post_id %>%
  filter(Arb_PersonId %in% (data %>% filter(Intervention == "Intervention") %>% distinct(Arb_PersonId) %>% pull(Arb_PersonId))) %>%
  filter(Intervention.factor == "Intervention")

## Create a list consisting of the two separate data sets ----
wpv_data <- list(bind_rows(wpv_con_ind, wpv_int_ind)
                 # bind_rows(wpv_con_an_all, wpv_int_an_all),
                 )

# Clear out objects from the workspace
rm(wpv_con_ind, wpv_int_ind, wpv_con_an_all, wpv_int_an_all)

# Create output table
tab2a <- wpv_data %>%
  purrr::map(
    ~ .x %>%
      mutate(#WPV_OBHPI = ifelse(WPV_OBHPI == 1 | WPV_WMQ == 1, 1, 0), # Combine OBHPI and WMQ
             WPV_vtype = ifelse(WPV_IP == 1 | WPV_TH == 1, 1, 0), # Combine WPV_IP and WPV_TH
             Intervention.factor = factor(Intervention.factor, levels = c("Control", "Intervention"))) %>%
      mutate(WPV_WMQ = ifelse(WPV_WMQ == 1 | WPV_PW_flow == 1, 1, 0)) %>%
      mutate(WPV_OBHPI = factor(WPV_OBHPI, levels = c("0", "1"))) %>%
      select(Intervention.factor,
             WPV_ICD,
             WPV_CC,
             WPV_OBHPI,
             WPV_WMQ,
             WPV_vtype,
             WPV_smart) %>%
      tbl_summary(by = Intervention.factor,
                  label = list(WPV_CC ~ "Chief Complaint",
                               WPV_ICD ~ "ICD Codes",
                               WPV_OBHPI ~ "OBHPI",
                               WPV_WMQ ~ "Weight management questionnaire",
                               WPV_vtype ~ "PW Visit Type",
                               WPV_smart ~ "PATHWEIGH Smart Set"),
                  value = list(WPV_OBHPI ~ "1"),
                  missing = "no",
                  digits = everything() ~ c(0,1)) %>% add_ci()
    )
```

```{r}
tab2b <-
  c("Control", "Intervention") %>%
    purrr::map_df(
      ~visits_post_id %>%
        filter(Arb_PersonId %in% (data %>% filter(Intervention == .x) %>% distinct(Arb_PersonId) %>% pull(Arb_PersonId))) %>%
        filter(IndexVisit == 1,
               Intervention.factor == .x) %>%
        select(
          Intervention.factor,
          Ref_BariatricSurgery:Ref_WellnessClinic,
          BariatricSurgery,
          N_Meds_AOM) %>%
        mutate(across(N_Meds_AOM, ~ifelse(. >= 1, 1, 0)),
               Intervention.factor = factor(Intervention.factor, levels= c("Control", "Intervention")))
    ) %>%
    tbl_summary(
      by = Intervention.factor,
      missing = "ifany",
      label = list(
        Ref_BariatricSurgery ~ "Referral to bariatric surgery",
        Ref_BehavioralHealth ~ "Referral to behavioral health",
        Ref_Dietician ~ "Referral to dietician",
        Ref_Endo ~ "Referral to endocrinology",
        Ref_WellnessClinic ~ "Referral to wellness clinic",
        BariatricSurgery ~ "Bariatric surgery",
        N_Meds_AOM ~ "Anti-obesity medications"),
      digits = list(all_categorical() ~ c(0,1),
                    all_continuous() ~ c(1,1))) %>% add_ci()
```

```{r}
tbls <- list(tab2a[[1]], tab2b) # because tab2a is a list, needs to be indexed

tbl_stack(tbls) %>%
  modify_header(
      stat_1 = "**Control**",
      stat_2 = "**Intervention**"
  ) %>%
  as_gt()
```

# Figure: Clinic Engagement
```{r}
clinic_engagement <- read_csv("D:/PATHWEIGH/working_files/clinic_engagement.csv", col_types = cols())
```

```{r}
# Drop any aberrant rows that may have been loaded, but not necessarily part
# of the data set of interest.
clinic_engagement %<>%
  drop_na(DeptNameEpicId)

# Update the clinic visit counts in mod_data and merge with clinic_engagement
clinic_engagement %<>%
  select(DepartmentEpicId:Engagement)

# Get the Cohort values to join in to clinic engagement for grouping
cohort_vals <- visits_post_id %>%
  select(DepartmentEpicId, GroupID) %>%
  distinct() %>%
  rename(Cohort = GroupID) %>%
  filter(DepartmentEpicId %in% clinic_engagement$DepartmentEpicId)

# Join cohort values
clinic_engagement %<>%
  left_join(., cohort_vals, by = "DepartmentEpicId")
```

```{r}
# Number of clinics per cohort
cohort_n <- clinic_engagement %>%
  group_by(Cohort) %>%
  count() %>%
  mutate(Cohort_n = str_c(Cohort, ": n = ", n))
```

```{r}
# Histogram as percentages
hist <- clinic_engagement %>%
    left_join(., cohort_n, by = "Cohort") %>%
    select(Engagement, Cohort_n) %>%
    mutate(Engagement = factor(Engagement),
           Cohort = factor(Cohort_n))
```

```{r, warning=FALSE, message=FALSE, fig.dpi = 600, fig.width=6.5, fig1}
# Calculate percentage where the denominator is total in each respective cohort
hist %>%
  group_by(Cohort, Engagement) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  ggplot(., aes(x = Engagement, y=freq, fill=Cohort)) +
  geom_bar(stat="identity",position=position_dodge2(preserve = "single")) +
  scale_y_continuous(labels = scales::label_percent()) +
  theme_minimal() +
  ylab("Percentage of clinics within cohort") +
  scale_fill_brewer(palette="Set2")
```
Caption: Engagement scores defined as the sum of 8 binary indicator of measures of engagement. Measures of engagement include 1) Zoom intro meeting, 2) In-person clinic visit from a member of the PATHWEIGH team, 3) Requested support from PATHWEIGH clinical team, 4) Used PATHWEIGH e-Learning module, 5) WOF training, 6) use of PATHWEIGH Placard, 7) Attended learning community, 8) Chose practice champion.

# ITT model
```{r}
# Redefine slope 1 and slope 2
pp_mod_data %<>%
  mutate(slope1 = ifelse(Intervention == "Control", 1, 0),
         slope2 = ifelse(Intervention == "Intervention", 1, 0)
         )
```

```{r}
# Create binary variables to be able to create the average visit for prediciton
pp_mod_data %<>%
  mutate(age_lt_45 = ifelse(Age_cat == "<=45", 1, 0),
         age_45_to_60 = ifelse(Age_cat == "45-60", 1, 0),
         age_gt_60 = ifelse(Age_cat == ">60", 1, 0),
         sex_m = ifelse(Sex == "Male", 1, 0),
         sex_f = ifelse(Sex == "Female", 1, 0),
         reth_nhw = ifelse(Race_Ethnicity == "Non-Hispanic White", 1, 0),
         reth_his = ifelse(Race_Ethnicity == "Hispanic or Latino", 1, 0),
         reth_blk = ifelse(Race_Ethnicity == "Black or African American", 1, 0),
         reth_asn = ifelse(Race_Ethnicity == "Asian", 1, 0),
         reth_oth = ifelse(Race_Ethnicity == "Other", 1, 0),
         reth_ukn = ifelse(Race_Ethnicity == "Unknown", 1, 0),
         year_at_ind0 = ifelse(Year_at_ind == "Year0", 1, 0),
         year_at_ind1 = ifelse(Year_at_ind == "Year1", 1, 0),
         year_at_ind2 = ifelse(Year_at_ind == "Year2", 1, 0),
         year_at_ind3 = ifelse(Year_at_ind == "Year3", 1, 0))
```

```{r}
# Linear mixed model with binary variables
lmer_mod_bin <- lmerTest::lmer(Weight_dv ~

          # age
          age_45_to_60 + age_gt_60 +

          # sex
          sex_m +

          # race ethnicity
          reth_his + reth_blk + reth_asn + reth_oth + reth_ukn +

          # year at index
          year_at_ind1 + year_at_ind2 + year_at_ind3 +

          # Weight at baseline
          Weight_bl + slope1 +

          # Slope1 is the same as Phase/Intervention group
          slope1:N_days_post_id + slope1:N_days_post_180 +

          # Slope2 is the opposi
          slope2:N_days_post_id + slope2:N_days_post_180 +

          # Clustering, convergence issues with both dept and personid
          # (1| DepartmentExternalName) + (1| Arb_PersonId),
          (1| Arb_PersonId),

          # Input data frame
          data=pp_mod_data
          )

# broom.mixed::tidy(lmer_mod_bin)
```

# Table: Model Output
```{r}
model_output <- broom.mixed::tidy(lmer_mod_bin,
                                  effects = "fixed",
                                  conf.int = TRUE
                                  )
```

```{r}
tab <- prep_mdl_out(model_output)

# Clean up the terms containing "slope" since each model will have different
# meanings for slope 1, or 2, or 3
tab %<>%
  mutate(term = str_replace(term, "slope1", "Control"),
         term = str_replace(term, "slope2", "Intervention")
  )
```

```{r}
# Grab slopes in the output table before converting to gt table
slopes <-
  tab %>%
  filter(grepl(":", term)) %>%
  select(term, estimate)

# Create a wide data frame with the 0-6m slope and 6-18m slope as separate cols
# estimate refers to 0-6m and post_180 is the 6-18m slope
slopes <- left_join(
  # Get the first interaction slope
  (slopes %>%
    mutate(group = c("Con", "Con", "Int", "Int")) %>%
    group_by(group) %>%
    slice_head() %>%
    ungroup()),
    # Get the estimates for 6-18m slope, by summing within interaction group
  (slopes %>%
    mutate(group = c("Con", "Con", "Int", "Int")) %>%
    group_by(group) %>%
    summarise(post_180_estimate = sum(estimate))),
  by = "group"
 ) 
```

```{r}
tab %>%
  fmt_tab(., "ITT Model")
```

## Figure: Model figure
```{r}
# Create figure of observed vs predicted values
obs_pred <- 
  bind_cols(pp_mod_data,
          (broom.mixed::augment(lmer_mod_bin) %>% select(.fixed))) %>%
  mutate(observed = Weight_dv,
         predicted = .fixed) %>%
  select(Arb_PersonId, N_months_post_id, observed, predicted, Intervention)
```

### All panels display predicted values from the ITT model.
```{r, fig.height = 4.2, fig.width=6.5, fig.dpi = 600}
ylims <- c(100, 113)

# *** pan_a may be obsolete in version 2
pan_a <- obs_pred  %>%
  group_by(Intervention, N_months_post_id) %>%
  summarise(across(observed:predicted, ~ mean(.x, rm.na = TRUE)), .groups = "drop") %>%
  pivot_longer(cols = observed:predicted, names_to = "Type", values_to = "Avg_Weight_kgs") %>%
  filter(Type == "observed") %>%
  ggplot(., aes(x = N_months_post_id, y = Avg_Weight_kgs)) +
  geom_line() +
  facet_wrap(~Intervention) +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0,18,3)) +
  ylim(ylims) +
  ylab("Average weight (kgs)") +
  xlab("Months after index visit")
```

```{r}
# Create the overlay data by averaging across all visits in each phase of the
# modeling data frame. Represents the non-index/followup visits. Since 
# covariates are time invarying within phase, it's not necessary to capture the 
# index visit
overlay_data <- 
pp_mod_data %>%
  select(age_lt_45, age_45_to_60, age_gt_60, sex_m,
       reth_his, reth_blk, reth_asn, reth_oth, reth_ukn,
       year_at_ind1, year_at_ind2, year_at_ind3,
       Weight_bl, slope1, slope2, Phase,
       N_days_post_id, N_days_post_180) %>%
  group_by(Phase) %>%
  summarise_all(mean, .groups = "drop") %>%
  slice(rep(1:n(), each = 3)) %>%
  mutate(N_days_post_id = rep(c(0,180,540), 2)) %>%
  mutate(N_days_post_180 = rep(c(0,0,360),2))
```


```{r, message = FALSE}
# Convert to regular data frame
# overlay_data <- data.frame(overlay_data)

# Get the predicted values for the blue line
# re.form = NA specifies fixed effects only
# predicted <- predict(lmer_mod_bin, 
#                      overlay_data, 
#                      re.form = NA, 
#                      type = "response")


# Create a data frame of the plotting data
# overlay_data <-
#   bind_cols(overlay_data, data.frame(predicted))

# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Here is where to introduce the functions for getting the prediction intervals
# predict function for bootstrapping
# Code from Dean Marchiori
# https://www.deanmarchiori.com/posts/2023-02-06-prediction-intervals-for-linear-mixed-effects-models/

# Set whether or not to run the boot strap
run_boot = FALSE

if (run_boot == TRUE) {
  
  predfn <- function(.) {
    predict(., newdata=new, re.form=NA)
    }

  # summarise output of bootstrapping
  sumBoot <- function(merBoot) {
    return(
      data.frame(fit = apply(merBoot$t, 2, function(x) as.numeric(quantile(x, probs=.5, na.rm=TRUE))),
                 lwr = apply(merBoot$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE))),
                 upr = apply(merBoot$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
      )
    )
  }
  
  # 'new' data because predfn requires the input to be named "new"
  new <- overlay_data

  # Save bootstrap products a bootMer object
  tictoc::tic()
  boot <- lme4::bootMer(lmer_mod_bin, predfn, nsim=1000, use.u=TRUE, type="parametric")
  tictoc::toc()

  # Apply the sumBoot function on the bootMerObject
  intervals <- sumBoot(boot)
  
  # Save boot strap output to not have to run it every single time we want a 
  # report
  write_csv(intervals,
            here::here(str_c("delivery_", delivery), 
                       "manuscript_tbls_figs/bootMer_intervals_itt.csv")
            )
  
} else {
  
  # Load the intervals file 
  intervals = read_csv(here::here(str_c("delivery_", delivery), 
                       "manuscript_tbls_figs/bootMer_intervals_itt.csv"))
}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```


```{r}
# Merge in the lwr and upr intervals to overlay_data
overlay_data <- bind_cols(
  overlay_data,
  # intervals %>% select(-fit) # Does not use the fit values
  intervals)

# Create a second data frame with the column names matching those required
# by original plot
overlay_data <- overlay_data %>%
  select(N_days_post_id, fit, lwr, upr, slope1) %>%
  pivot_longer(cols = fit:upr, 
               names_to = "Type", 
               values_to = "Avg_Weight_kgs") %>%
  rename(N_months_post_id = N_days_post_id) %>%
  mutate(Intervention = ifelse(slope1 == 1, "Control", "Intervention")) %>%
  mutate(N_months_post_id = ifelse(N_months_post_id == 180, 6, 
                                   ifelse(N_months_post_id == 540, 18, 0))) %>%
  select(Intervention, N_months_post_id, Type, Avg_Weight_kgs)
```

```{r}
# Slopes data captured upstream in Table: Model Output section
slopes %<>%
  mutate(lab = str_c("Rate of change\n0-6mo: ", estimate, " kg/month\n6-18mo: ", post_180_estimate, " kg/month")) %>%
  mutate(Avg_Weight_kgs = ifelse(term == "Control:N_months_post_id", 106, 106),
         N_months_post_id = 1.5,
         Intervention = ifelse(group == "Con", "Control", "Intervention"))
```

```{r, fig.height = 4.2, fig.width=6.5, fig.dpi = 600}
#| eval: false
# Plot of the 1st draft of the model plot with lines serving as indicators for 
# the upper an dlower prediction intervals.
# *** May become obsolete in version 2
pan_a +
  # geom_line(data = overlay_data %>% filter(Type == "predicted"), color = "blue") +
  geom_line(data = overlay_data %>% filter(Type == "fit"), color = "blue") +
  geom_line(data = overlay_data %>% filter(Type == "lwr"), 
            color = "red", linetype = "dotted") +
  geom_line(data = overlay_data %>% filter(Type == "upr"), 
            color = "red", linetype = "dotted")
```

```{r, fig.height = 4.2, fig.width=6.5, fig.dpi = 600}
# Plot of the 2nd draft. Instead of superimposing geom_ribbon(), this version
# superimposes geom_line() of the observed values
observed <- obs_pred %>%
  group_by(Intervention, N_months_post_id) %>%
  summarise(across(observed:predicted, ~ mean(.x, rm.na = TRUE)), .groups = "drop") %>%
  pivot_longer(cols = observed:predicted, names_to = "Type", values_to = "Avg_Weight_kgs") %>%
  filter(Type == "observed") %>%
  mutate(fit = Avg_Weight_kgs) %>%
  select(-Type, Avg_Weight_kgs)

# fit refers to the predicted values at 0, 6, and 18 months
# lwr refers to the lower bound of the fit values
# upr refers to the upper bound of the fit values
overlay_data %>%
  group_by(Intervention, N_months_post_id) %>%
  pivot_wider(names_from = Type, values_from = Avg_Weight_kgs) %>%
  ggplot(., aes(x = N_months_post_id, y = fit)) +
  geom_line(aes(N_months_post_id, fit), color = "blue") +
  geom_ribbon(aes(ymin = lwr, ymax = upr), fill = "red", alpha = 0.1, show.legend = FALSE) +
  facet_grid(~ Intervention) +
  geom_line(data = observed, color = "black") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0,18,3)) +
  ylim(ylims) +
  ylab("Average weight (kgs)") +
  xlab("Months after index visit") +
  geom_text(data = slopes, 
            aes(x = N_months_post_id, 
                y = Avg_Weight_kgs, 
                label = lab,
                hjust = "left"),
                size = 2)
```

```{r}
# Used in the development of the algorithm for generating the prediction
# intervals
# write_csv(tab, 
#           here::here(str_c("delivery_", delivery), "manuscript_tbls_figs/lmer_mod_output.csv")
#           )
# 
# write_csv(slopes, 
#           here::here(str_c("delivery_", delivery), "manuscript_tbls_figs/slopes.csv")
#           )
# 
# write_csv(overlay_data, 
#           here::here(str_c("delivery_", delivery), "manuscript_tbls_figs/overlay_data.csv")
#           )
```


# 4-slopes model
```{r}
# V1 Code
# Redefine slope 1, slope 2, slope 3 in pp_mod_data to model three groups
# Slope 1 is control no pw
# Slope 2 is control w pw
# Slope 3 is intervention no pw
# Slope 4 is intervention w pw
pp_mod_data %<>%
  mutate(pw_visit = pw,
         pw_pat = ifelse(
           Arb_PersonId %in% (pp_mod_data %>% 
                                filter(pw == 1) %>% 
                                pull(Arb_PersonId)
                              ), 1, 0),
         slope1 = ifelse(pw_pat == 0 & Intervention == "Control", 1, 0),
         slope2 = ifelse(pw_pat == 1 & Intervention == "Control", 1, 0),
         slope3 = ifelse(pw_pat == 0 & Intervention == "Intervention", 1, 0),
         slope4 = ifelse(pw_pat == 1 & Intervention == "Intervention", 1, 0),
         )
```


```{r}
# pw is a visit indicator
# need PW as a patient indicator
pp_mod_data %>%
  group_by(Arb_PersonId, Intervention) %>%
  slice_head() %>%
  ungroup() %>%
  select(pw_pat, Intervention) %>%
  tbl_summary(by = Intervention) %>%
  as_gt()
```

```{r}
# V1 Code
# 4 Slopes Model
# PP model with patients that have both control and intervention visits
# Linear mixed model with binary variables
lmer_mod_bin4 <- lmerTest::lmer(Weight_dv ~

          # age
          age_45_to_60 + age_gt_60 +

          # sex
          sex_m +

          # race ethnicity
          reth_his + reth_blk + reth_asn + reth_oth + reth_ukn +

          # year at index
          year_at_ind1 + year_at_ind2 + year_at_ind3 +

          # Weight at baseline
          Weight_bl + pw_pat + Phase +

          # Slope1 is control no pw
          slope1:N_days_post_id + slope1:N_days_post_180 +

          # Slope2 is control pw
          slope2:N_days_post_id + slope2:N_days_post_180 +

          # 3 - Intervention group no PW
          slope3:N_days_post_id + slope3:N_days_post_180 +
            
          # 4 - Intervention group PW
          slope4:N_days_post_id + slope4:N_days_post_180 +

          # Clustering on personid
          (1| Arb_PersonId),

          # Input data frame
          data=pp_mod_data
          )
```

```{r}
# V1 Code
# Create figure of observed vs predicted values
predicted <- predict(lmer_mod_bin4, pp_mod_data, re.form=NA, type="response")

obs_pred <- bind_cols(pp_mod_data, data.frame(predicted)) %>%
  mutate(observed = Weight_dv)
```

# Table: Model Output
```{r}
# V2 Code, adds confidence intervals for parameter estimates
model_output <- broom.mixed::tidy(lmer_mod_bin4,
                                  effects = "fixed",
                                  conf.int = TRUE
                                  )
```

```{r}
# V1 Code
# Prep the model output
tab <- prep_mdl_out(model_output)

# Manually modify the slope terms
tab %<>%
  mutate(term = str_replace(term, "slope1", "Con_nPW"),
         term = str_replace(term, "slope2", "Con_PW"),
         term = str_replace(term, "slope3", "Int_nPW"),
         term = str_replace(term, "slope4", "Int_PW")
         ) 
```

```{r}
# V1 Code
# Grab slopes in the output table before converting to gt table
slopes <- tab %>%
  filter(grepl(":", term)) %>%
  select(term, estimate)

slopes <- left_join(
(slopes %>%
  mutate(group = c("Con_nPW", "Con_nPW", "Con_PW", "Con_PW", "Int_nPW", "Int_nPW", "Int_PW", "Int_PW")) %>%
  group_by(group) %>%
  slice_head() %>%
  ungroup()),
# Get the estimates for after 6 months
(slopes %>%
  mutate(group = c("Con_nPW", "Con_nPW", "Con_PW", "Con_PW", "Int_nPW", "Int_nPW", "Int_PW", "Int_PW")) %>%
  group_by(group) %>%
  summarise(post_180_estimate = sum(estimate))),
by = "group"
 ) 
```

```{r}
# V1 Code
# Add grouping rows for the following terms
tab %>%
  fmt_tab(., "4-Slope Model")
```

### Figure: All panels display predicted values from 4-slope model
Compares two groups in both phases. nPW group never received any of the PATHWEIGH tools during any of their intervention visits. The PW group received at least one PATHWEIGH tool in at least one visit during the intervention phase.

```{r, fig.height = 6, fig.width=6.5, fig.dpi = 600}
# V1 Code
# 3-line plot of the per-protocol model
pan_b <- obs_pred %>%
  mutate(group = ifelse(slope1 == 1, "Con_nPW", NA),
         group = ifelse(slope2 == 1, "Con_PW", group),
         group = ifelse(slope3 == 1, "Int_nPW", group),
         group = ifelse(slope4 == 1, "Int_PW", group)) %>%
  select(Arb_PersonId, N_months_post_id, observed, predicted, Intervention, group) %>%
  group_by(group, Intervention, N_months_post_id) %>%
  summarise(across(observed:predicted, ~ mean(.x, rm.na = TRUE)), .groups = "drop") %>%
  pivot_longer(cols = observed:predicted, names_to = "Type", values_to = "Avg_Weight_kgs") %>%
  filter(Type == "observed") %>% # to display only observed values instead of observed and predicted
  ggplot(., aes(x = N_months_post_id, y = Avg_Weight_kgs)) +
  geom_line() +
  facet_wrap(~group) +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0,18,3)) +
  ylim(ylims)
```

```{r}
# V1 Code
# Create the overlay data by averaging across all visits in each phase of the
# modeling data frame. Represents the non-index/followup visits. Since covariates
# are time invarying within phase, it's not necessary to capture the index visit
overlay_data <-
pp_mod_data %>%
  mutate(group = ifelse(slope1 == 1, "Con_nPW", NA),
         group = ifelse(slope2 == 1, "Con_PW", group),
         group = ifelse(slope3 == 1, "Int_nPW", group),
         group = ifelse(slope4 == 1, "Int_PW", group)) %>%
  select(age_lt_45, age_45_to_60, age_gt_60, sex_m,
       reth_his, reth_blk, reth_asn, reth_oth, reth_ukn,
       year_at_ind1, year_at_ind2, year_at_ind3,
       Weight_bl, slope1, slope2, slope3, slope4,
       N_days_post_id, N_days_post_180, group,
       pw_pat, Phase) %>%
  group_by(group) %>%
  summarise_all(mean, .groups = "drop")

# overlay_data %>%
#   gt::gt()
```

```{r}
# V1 Code
# Model predictions are done with N_days_post_* not N_months
# duplicate rows to make predictions as 0, 6, and 18 months
# Average visit in each phase at three different timepoints
overlay_data %<>%
  slice(rep(1:n(), each = 3)) %>%
  mutate(N_days_post_id = rep(c(0,180,540), 4)) %>%
  mutate(N_days_post_180 = rep(c(0,0,360), 4))
# 
# overlay_data %>%
#   gt::gt()
```

```{r}
# Get the predicted values on the average visit in each group
predicted <- predict(lmer_mod_bin4, overlay_data, re.form = NA, type = "response")

# Create a data frame of the plotting data
overlay_data <-
  bind_cols(overlay_data, data.frame(predicted))

# Create a second data frame with the column names matching those required
# by original plot
overlay_data %<>%
  select(N_days_post_id, predicted, group) %>%
  rename(N_months_post_id = N_days_post_id,
         Avg_Weight_kgs = predicted) %>%
  mutate(N_months_post_id = rep(c(0, 6, 18), 4),
         Type = "predicted") %>%
  select(group, N_months_post_id, Type, Avg_Weight_kgs)
```

```{r, fig.height = 4.2, fig.width=6.5, fig.dpi = 600}
# 3 slopes plot with blue trend lines only
# pan_b +
#   geom_line(data = overlay_data, color = "blue")
```

```{r}
# Slopes data captured upstream in Table: Model Output section
# The Avg_Weight_kgs values of 104;110 are used as x-y coordinates to place the
# element text to display the slopes
slopes %<>%
  mutate(lab = str_c("Rate of change\n0-6mo: ", estimate, " kg/month\n6-18mo: ", post_180_estimate, " kg/month")) %>%
  mutate(Avg_Weight_kgs = ifelse(group == "Con_nPW", 104, NA),
         Avg_Weight_kgs = ifelse(group == "Con_PW", 110, Avg_Weight_kgs),
         Avg_Weight_kgs = ifelse(group == "Int_nPW", 104, Avg_Weight_kgs),
         Avg_Weight_kgs = ifelse(group == "Int_PW", 110, Avg_Weight_kgs),
         N_months_post_id = 1.5)
```


```{r, fig.height = 4.2, fig.width=6.5, fig.dpi = 600}
#| eval: false
pan_b +
  geom_line(data = overlay_data, color = "blue") +
  geom_text(data = slopes, 
            aes(x = N_months_post_id, 
                y = Avg_Weight_kgs, 
                label = lab,
                hjust = "left"),
                size = 2)
```
<!-- # ------------REGION BEGIN --------------- -->
```{r}
# Create a new overlay data frame to begin with
overlay_data <-
pp_mod_data %>%
  mutate(group = ifelse(slope1 == 1, "Con_nPW", NA),
         group = ifelse(slope2 == 1, "Con_PW", group),
         group = ifelse(slope3 == 1, "Int_nPW", group),
         group = ifelse(slope4 == 1, "Int_PW", group)) %>%
  select(age_lt_45, age_45_to_60, age_gt_60, sex_m,
       reth_his, reth_blk, reth_asn, reth_oth, reth_ukn,
       year_at_ind1, year_at_ind2, year_at_ind3,
       Weight_bl, slope1, slope2, slope3, slope4,
       N_days_post_id, N_days_post_180, group,
       pw_pat, Phase) %>%
  group_by(group) %>%
  summarise_all(mean, .groups = "drop") %>%
  slice(rep(1:n(), each = 3)) %>%
  mutate(N_days_post_id = rep(c(0,180,540), 4)) %>%
  mutate(N_days_post_180 = rep(c(0,0,360),4))
```

```{r, message = FALSE}
# Set whether or not to run the boot strap
run_boot = FALSE

if (run_boot == TRUE) {
  
  predfn <- function(.) {
    predict(., newdata=new, re.form=NA)
    }

  # summarise output of bootstrapping
  sumBoot <- function(merBoot) {
    return(
      data.frame(fit = apply(merBoot$t, 2, function(x) as.numeric(quantile(x, probs=.5, na.rm=TRUE))),
                 lwr = apply(merBoot$t, 2, function(x) as.numeric(quantile(x, probs=.025, na.rm=TRUE))),
                 upr = apply(merBoot$t, 2, function(x) as.numeric(quantile(x, probs=.975, na.rm=TRUE)))
      )
    )
  }
  
  # 'new' data because predfn requires the input to be named "new"
  new <- overlay_data

  # Save bootstrap products a bootMer object
  tictoc::tic()
  boot <- lme4::bootMer(lmer_mod_bin4, predfn, nsim=1000, use.u=TRUE, type="parametric")
  tictoc::toc()

  # Apply the sumBoot function on the bootMerObject
  intervals <- sumBoot(boot)
  
  # Save boot strap output to not have to run it every single time we want a 
  # report
  write_csv(intervals,
            here::here(str_c("delivery_", delivery), 
                       "manuscript_tbls_figs/bootMer_intervals_pp.csv")
            )
  
} else {
  
  # Load the intervals file 
  intervals = read_csv(here::here(str_c("delivery_", delivery), 
                       "manuscript_tbls_figs/bootMer_intervals_pp.csv"))
}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

```{r}
# Merge in the lwr and upr intervals to overlay_data
overlay_data <- bind_cols(
  overlay_data,
  # intervals %>% select(-fit) # Does not use the fit values
  intervals)
```

```{r}
observed <- 
  obs_pred %>%
  mutate(group = ifelse(slope1 == 1, "Con_nPW", NA),
         group = ifelse(slope2 == 1, "Con_PW", group),
         group = ifelse(slope3 == 1, "Int_nPW", group),
         group = ifelse(slope4 == 1, "Int_PW", group)) %>%
  group_by(group, N_months_post_id) %>%
  summarise(across(observed:predicted, ~ mean(.x, rm.na = TRUE)), .groups = "drop") %>%
  pivot_longer(cols = observed:predicted, names_to = "Type", values_to = "Avg_Weight_kgs") %>%
  filter(Type == "observed") %>%
  mutate(fit = Avg_Weight_kgs) %>%
  select(-Type, Avg_Weight_kgs)
```


```{r, fig.height = 4.2, fig.width=6.5, fig.dpi = 600}
# Create a second data frame with the column names matching those required
# by original plot
overlay_data %>%
  select(N_days_post_id, fit, lwr, upr, group) %>%
  rename(N_months_post_id = N_days_post_id) %>%
  mutate(N_months_post_id = ifelse(N_months_post_id == 180, 6, 
                                 ifelse(N_months_post_id == 540, 18, 0))) %>%
  ggplot(., aes(x = N_months_post_id, y = fit), color = "blue") +
  geom_line(aes(N_months_post_id, fit), color = "blue") +
  geom_ribbon(aes(ymin = lwr, ymax = upr), fill = "red", alpha = 0.1, show.legend = FALSE) +
  facet_wrap(~ group) +
    geom_line(data = observed, color = "black") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0,18,3)) +
  ylim(ylims) +
  ylab("Average weight (kgs)") +
  xlab("Months after index visit") +
  geom_text(data = slopes, 
            aes(x = N_months_post_id, 
                y = Avg_Weight_kgs, 
                label = lab,
                hjust = "left"),
                size = 2)
```
# Comparison of index and last visits
```{r}
ind_vs_lv <- 
bind_rows(
(visits_post_id %>%
  filter(Arb_PersonId %in% data$Arb_PersonId, 
         IndexVisit == 1)),
(visits_post_id %>%
  filter(Arb_PersonId %in% data$Arb_PersonId, 
         LastVisit == 1))
) %>%
  mutate(Visit = factor(ifelse(IndexVisit == 1, "Index Visit", "Final Visit"), levels = c("Index Visit", "Final Visit"))) %>%
  mutate(Intervention.factor = factor(Intervention.factor, levels = c("Control", "Intervention"))) %>%
  mutate(Smoking_Status = fct_na_value_to_level(Smoking_Status, level = "Unknown")) %>%
  select(Arb_PersonId, Age, Sex, Race_Ethnicity, Insurance, BMI,
         Systolic_blood_pressure, Diastolic_blood_pressure,
         A1C:TSH, -`Cystatin C`, EOSS,
         PHQ2, PHQ9, GAD7, Smoking_Status,
         Intervention.factor, Visit,
         N_days_post_id, N_months_post_id)
```

## A1C
### A1C ~ Visit * Intervention.factor + (1|Arb_PersonId)
```{r}
broom.mixed::tidy(
  lmerTest::lmer(
    A1C ~ Visit * Intervention.factor + (1| Arb_PersonId),
    data = ind_vs_lv),
  conf.int = TRUE, effects = "fixed")  %>%
  as_tibble() %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  gt::gt()
```

### A1C ~ Visit:Intervention.factor + Visit:(1-Intervention.factor) + Intervention.factor + (1| Arb_PersonId)
```{r}
# A1C not significant
# A1C ~ Visit*Intervention.factor
broom.mixed::tidy(
  lmerTest::lmer(
    A1C ~ Visit:Intervention.factor + Visit:(1-Intervention.factor) + Intervention.factor + (1| Arb_PersonId),
    # A1C ~ Visit*Intervention.factor + (1| Arb_PersonId),
    data = ind_vs_lv),
  conf.int = TRUE, effects = "fixed")  %>%
  as_tibble() %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  gt::gt()
```

## Triglycerides
### Triglycerides ~ Visit * Intervention.factor + (1|Arb_PersonId)
```{r}
broom.mixed::tidy(
  lmerTest::lmer(
    Triglycerides ~ Visit * Intervention.factor + (1|Arb_PersonId),
    data = ind_vs_lv),
  conf.int = TRUE, effects = "fixed")  %>%
  as_tibble() %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  gt::gt()
```

### Triglycerides ~ Visit:Intervention.factor + Visit:(1-Intervention.factor) + Intervention.factor + (1| Arb_PersonId)
```{r}
broom.mixed::tidy(
  lmerTest::lmer(
    Triglycerides ~ Visit:Intervention.factor + Visit:(1-Intervention.factor) + Intervention.factor + (1| Arb_PersonId),
    data = ind_vs_lv),
  conf.int = TRUE, effects = "fixed")  %>%
  as_tibble() %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  gt::gt()
```

## BMI
### BMI ~ Visit * Intervention.factor + (1| Arb_PersonId)
```{r}
broom.mixed::tidy(
  lmerTest::lmer(
    BMI ~ Visit * Intervention.factor + (1| Arb_PersonId),
    data = ind_vs_lv),
  conf.int = TRUE, effects = "fixed")  %>%
  as_tibble() %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  gt::gt()
```

### BMI ~ Visit:Intervention.factor + Visit:(1-Intervention.factor) + Intervention.factor + (1| Arb_PersonId)
```{r}
broom.mixed::tidy(
  lmerTest::lmer(
    BMI ~ Visit:Intervention.factor + Visit:(1-Intervention.factor) + Intervention.factor + (1| Arb_PersonId),
    data = ind_vs_lv),
  conf.int = TRUE, effects = "fixed") %>%
  as_tibble() %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  gt::gt()
```

# Comorbidities
```{r}
# Supplement: Comorbidities ------------------------------------------------
# Table for the comorbidities of interest at the index visit
# The vector comorbidity_names comes from running the comorbidities script and
# can be read into R from the delivery's data folder.
ordered_comorbidity_names <-
visits_post_id %>%
  filter(Intervention.factor == "Control",
         IndexVisit == 1) %>%
  select(all_of(comorbidity_names)) %>%
  summarise_all(list(sum)) %>%
  pivot_longer(., cols = everything(), names_to = "comorbidity", values_to = "n") %>%
  arrange(desc(n)) %>%
  filter(n > 1) %>%
  pull(comorbidity)
```

```{r}
# This table displays the exact numbers for control and intervention
c("Control", "Intervention") %>%
  purrr::map_df(
    ~visits_post_id %>%
      filter(Arb_PersonId %in% (data %>% filter(Intervention == .x) %>% distinct(Arb_PersonId) %>% pull(Arb_PersonId))) %>%
      filter(IndexVisit == 1,
              Intervention.factor == .x) %>%
      select(all_of(ordered_comorbidity_names), Intervention.factor) %>%
      mutate(Intervention.factor = factor(Intervention.factor, levels = c("Control", "Intervention")))
      # mutate(across(all_of(ordered_comorbidity_names), ~ factor(., levels = c("0", "1"))))
  ) %>%
  tbl_summary(by = "Intervention.factor",
              digits = everything() ~ 1) %>%
  # modify_header(stat_1 = "**Control**",
  #               stat_2 = "**Intervention**") %>%
  as_gt()
```

# Supplementary Table 2. 

Patient demographics and health metrics at the index visit for control and intervention phases for all enrolled patients
```{r}
supp_2 <- 
  visits_post_id %>%
  filter(IndexVisit == 1) %>%
  mutate(Intervention.factor = factor(Intervention.factor, 
                                      levels = c("Control", "Intervention"))) %>%
  mutate(Smoking_Status = fct_na_value_to_level(Smoking_Status, level = "Unknown")) %>%
  select(Age, Weight_kgs, Sex, Race_Ethnicity, Insurance, BMI,
         Systolic_blood_pressure, Diastolic_blood_pressure,
         A1C:TSH, -`Cystatin C`, EOSS,
         PHQ2, PHQ9, GAD7, Smoking_Status,
         Intervention.factor) %>%
  tbl_summary(by = Intervention.factor,
                  missing = "ifany",
                  type = list(c(PHQ2, PHQ9, GAD7) ~ 'continuous'),
                  # statistic = list(all_continuous() ~ c("{mean} ({sd}; {min}; {max})")),
                  statistic = list(all_continuous() ~ c("{mean} ({sd})")),
                  label = list(Age ~ "Age (years)",
                               Weight_kgs ~ "Weight (kg)",
                               Race_Ethnicity ~ "Race/Ethnicity",
                               BMI ~ "BMI (kg/m^2)",
                               Systolic_blood_pressure ~ "Systolic BP (mmHg)",
                               Diastolic_blood_pressure ~ "Diastolic BP (mmHg)",
                               Smoking_Status ~ "Smoking Status"),
                  digits = list(all_categorical() ~ c(0,1),
                                  all_continuous() ~ c(1,1)))

# Leigh wants to not display the sample size and instead state it in a caption
# tab1 %<>%
#   modify_header(stat_1_1 = "**Index Visit**",
#                 stat_2_1 = "**Final Visit**",
#                 stat_1_2 = "**Index Visit**",
#                 stat_2_2 = "**Final Visit**")

supp_2 %>% 
  as_gt()
```

# Sensitivity analyses

ITT model using all eligible and enrolled patients
```{r}

```

