---
title: "PATHWEIGH Statistical Model Development"
format:
  html:
    toc: true
    embed-resources: true
    # grid:
    #   sidebar-width: 0px
    #   body-width: 2000px
    #   margin-width: 0px
    #   gutter-width: 1.5rem
      
editor: source
---


```{r}
#| echo: false
# Carlos Rodriguez PhD. CU Dept. of Family Medicine
# Control Phase Models - Development of the statistical model for the EE and 
# ENE subgroups in both control and intervention phases.
```

```{r, load packages}
#| echo: false
pacman::p_load(here,         # For managing directory paths
               magrittr,     # For the assignment pipe operator %<>%
               tidyverse,    # For data manipulation tools
               data.table,   # For reading .csv files
               openxlsx,     # For reading .xlsx files
               tictoc,       # For timing and benchmarking functions
               gtsummary,    # For tables
               DT,
               car,
               geepack,
               install = FALSE)
```


```{r}
#| echo: false

# Load generate_plot function --------------------------------------------------
# source(here("scripts/generate_model_plots.R"))
source("S:/FM/PATHWEIGH/Quantitative/Projects/dataset_20231010/scripts/generate_model_plots.R")

# Load processed data ----------------------------------------------------------
load(here("data/ee_ene_20231010.RData"))
# load(here("data/processed_visits_post_id_20231010.RData"))
# load(here("data/processed_all_visits_20231010.RData"))
```


```{r, echo = FALSE}
# Set up a data frame to subset the data and work off of
data <- ee_ene

# Drop rows where Sex is Unknown
# Only 12 as of 2/22/24
data %<>%
  filter(Sex != "Unknown")
```


```{r, echo = F}
# capture the patient ids for those that have more than 1 visit in the control
# phase to use in the modelling
con_ids_gt1_visits <-
  data %>%
  filter(Intervention == 0,
         Censored == 0) %>%
  group_by(Arb_PersonId) %>%
  count() %>%
  filter(n > 1) %>%
  pull(Arb_PersonId)


# capture the patient ids for those that have more than 1 visit in the intervention
# phase to use in the modelling
int_ids_gt1_visits <-
  data %>%
  filter(Intervention == 1,
         Censored == 0) %>%
  group_by(Arb_PersonId) %>%
  count() %>%
  filter(n > 1) %>%
  pull(Arb_PersonId)
```

```{r, echo = F}
# Declare data preparation function
prep_data <-  function(data){
  # Filter rows and select the columns necessary for modeling
  data %<>%
  select(Arb_PersonId,
         Arb_EncounterId,
         EncounterDate,
         DepartmentExternalName,
         IndexVisit,
         WPV,
         Weight_kgs,
         Age,
         Sex,
         Race_Ethnicity,
         Year,
         N_months_post_id,
         N_days_post_id,
         BMI,
         Intervention.factor,
         EE,
         Any) %>%

  # Turn WPV from count to a binary indicator
  mutate(WPV = ifelse(WPV > 0, 1, 0)) %>%

  # Calculate a cumulative sum for the WPV binary indicator
  group_by(Arb_PersonId) %>%
  arrange(EncounterDate) %>%
  mutate(N_prior_WPVs = cumsum(WPV)) %>%
  ungroup() %>%

  # Subtract 1 from encounters after the index to exclude the current WPV N_prior_WPVs
  # only if there are more than one N_prior visits. That way at minimum, all rows
  # have at least 1 prior visit, which should be the requirement since we filter
  # for patients that have more than one encounter with weight.
  mutate(N_prior_WPVs = ifelse(N_prior_WPVs > 1, N_prior_WPVs - 1, N_prior_WPVs)) %>%

  # Create weight baseline and weight dependent variables and Year at index visit variable
  mutate(Weight_bl = ifelse(IndexVisit == 1, Weight_kgs, NA),
         Weight_dv = ifelse(IndexVisit != 1, Weight_kgs, NA),
         Year_at_ind = ifelse(IndexVisit == 1, Year,NA)) %>%

  # Convert Weight_bl and Year_at_ind to time invariant variables
  group_by(Arb_PersonId) %>%
  fill(Weight_bl, .direction = "updown") %>%
  fill(Year_at_ind, .direction = "updown") %>%
  ungroup() %>%

  # Remove the index visits from the data set and any NA Weight_dv values
  filter(IndexVisit == 0) %>%
  drop_na(Weight_dv) %>%

  # Factor the Arb_PersonId variable and effect code the Year variable
  # mutate(Arb_PersonId = factor(Arb_PersonId),
  #        Year = case_when(
  #          Year == "Year0" ~ -1,
  #          Year == "Year1" ~ 0,
  #          Year == "Year2" ~ 1)) %>%
    
  # Factor Arb Person Id,
  # When incorporating intervention data, the code chunk above does not accomodate Year3
  mutate(Arb_PersonId = factor(Arb_PersonId)) %>%

  # Create a squared N_days_post_id variable
  mutate(N_days_post_id_sq = N_days_post_id^2) %>%

  # Categorize Age
  mutate(Age_cat = ifelse(Age <= 45, "<=45", NA),
         Age_cat = ifelse(Age > 45 & Age <= 60, "45-60", Age_cat),
         Age_cat = ifelse(Age > 60, ">60", Age_cat)) %>%

  mutate(Sex = relevel(factor(Sex), ref = "Female"),
         Age_cat = relevel(factor(Age_cat), ref = "45-60"),
         Race_Ethnicity = relevel(Race_Ethnicity, ref = "Non-Hispanic White"),
         Intervention = Intervention.factor) %>%
    
  select(-Intervention.factor) %>%

  # Filter observations to 18 months (540 days)
  filter(N_days_post_id <= 540)
  
  # Output of the function
  return(data)
  }
```


```{r, echo = F}
# Create the control data
mod_data_con <- 
  data %>%
  filter(Intervention == 0,
         Censored == 0,
         Arb_PersonId %in% con_ids_gt1_visits) %>%
  prep_data()
```


```{r, echo = F}
# Create the intervention data
mod_data_int <- 
    data %>%
    filter(Intervention == 1,
         Censored == 0,
         Arb_PersonId %in% int_ids_gt1_visits) %>%
  prep_data()
```


```{r, echo = F}
# Stack the two data frames together
mod_data <- bind_rows(mod_data_con, mod_data_int)


# Set reference for year at index
# reference set here since no encounter in intervention will have Year0 as year at index
mod_data %<>%
  mutate(Year_at_ind = relevel(factor(Year_at_ind), ref = "Year0"))

# Create number of days after index and after 6 months
mod_data %<>%
  # N_days_post_id less than (lt) 180 (6 months)
  mutate(bin_N_days_post_id_gt_180 = ifelse(N_days_post_id > 180, 1, 0),
         N_days_post_180 = bin_N_days_post_id_gt_180 * (N_days_post_id - 180))

# create a binary variable of those greater than 30 bmi
mod_data %<>%
  mutate(bmi_gt_30 = ifelse(BMI >= 30, 1, 0))
```


```{r, echo = F}
# Capture the age category and bmi category at the index visit to merge in as a time invariant variable
time_invariant_vars <- 
data %>%
  filter(Censored == 0,
         IndexVisit ==1,
         Arb_PersonId %in% mod_data$Arb_PersonId) %>%
  select(Arb_PersonId, Age, BMI, Intervention.factor) %>% 
  mutate(Age_cat = ifelse(Age <= 45, "<=45", NA),
         Age_cat = ifelse(Age > 45 & Age <= 60, "45-60", Age_cat),
         Age_cat = ifelse(Age > 60, ">60", Age_cat),
         bmi_gt_30 = ifelse(BMI >= 30, 1, 0),
         bmi_gt_35 = ifelse(BMI >= 35, 1, 0),
         bmi_gt_40 = ifelse(BMI >= 40, 1, 0),
         Arb_PersonId = factor(Arb_PersonId),
         Intervention = Intervention.factor) %>%
  select(-Age, -Intervention.factor)
  
# Recategorize age to a time invariant version
mod_data %<>%
  select(-Age_cat, -bmi_gt_30, -BMI) %>%
  left_join(.,
            time_invariant_vars,
            by = c("Arb_PersonId", "Intervention"))

# Set the reference for intervention and reorder Age_cat
mod_data %<>%
  mutate(Intervention = relevel(factor(Intervention), ref = "Control"),
         Age_cat = factor(Age_cat, levels = c("<=45", "45-60", ">60")),
         Race_Ethnicity = factor(Race_Ethnicity, levels = c("Non-Hispanic White", "Hispanic or Latino", "Black or African American", "Asian", "Other", "Unknown"))
)
```


```{r, echo = F, eval=F}
# Time invariant covariates linked to index date in each phase of the treatment
# Age_cat - could change across each intervention
mod_data %>%
  group_by(Arb_PersonId) %>%
  summarise(n = n_distinct(Age_cat)) %>%
  filter(n > 1) %>%
  nrow()

# Sex - Should not change across the intervention periods
# Should end up with 0 rows
mod_data %>%
  group_by(Arb_PersonId) %>%
  summarise(n = n_distinct(Sex)) %>%
  filter(n > 1) %>%
  nrow()

# Race - Should not change across the intervention periods
# Should end up with 0 rows
mod_data %>%
  group_by(Arb_PersonId) %>%
  summarise(n = n_distinct(Race_Ethnicity)) %>%
  filter(n > 1) %>%
  nrow()
```

# Eligible and Enrolled Patients - All records in mod_data
```{r}
#| echo: false
#| eval: true

# Counts any given individual in both intervention and control phase
mod_data %>%
  filter(EE == 1) %>%
  mutate(Race_Ethnicity = fct_na_value_to_level(Race_Ethnicity, level = "Unknown")) %>%
  select(Age, Sex, Race_Ethnicity, Intervention, Weight_bl, Weight_dv, BMI) %>%
  tbl_summary(by = Intervention,
              missing = "ifany",
              statistic = list(all_continuous() ~ c("{mean} ({sd})")),
              label = list(Race_Ethnicity ~ "Race/Ethnicity")) %>%
  add_overall() %>%
  as_flex_table() %>%
  flextable::autofit()
```

# Eligible and Enrolled Patients - One record per patient per intervention
```{r}
#| echo: false
#| eval: true
#| 
mod_data %>%
  filter(EE == 1) %>%
  group_by(Arb_PersonId, Intervention) %>%
  arrange(EncounterDate) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(Race_Ethnicity = fct_na_value_to_level(Race_Ethnicity, level = "Unknown")) %>%
  select(Age, Sex, Race_Ethnicity, Intervention, Weight_bl, Weight_dv, BMI) %>%
  tbl_summary(by = Intervention,
              missing = "ifany",
              statistic = list(all_continuous() ~ c("{mean} ({sd})")),
              label = list(Race_Ethnicity ~ "Race/Ethnicity")) %>%
  add_overall() %>%
  as_flex_table() %>%
  flextable::autofit()
```


# Eligible and Not Enrolled Patients - All records in mod_data
```{r}
#| echo: false
#| eval: true

# Counts any given individual in both intervention and control phase
mod_data %>%
  filter(EE == 0) %>%
  mutate(Race_Ethnicity = fct_na_value_to_level(Race_Ethnicity, level = "Unknown")) %>%
  select(Age, Sex, Race_Ethnicity, Intervention, Weight_bl, Weight_dv, BMI) %>%
  tbl_summary(by = Intervention,
              missing = "ifany",
              statistic = list(all_continuous() ~ c("{mean} ({sd})")),
              label = list(Race_Ethnicity ~ "Race/Ethnicity")) %>%
  add_overall() %>%
  as_flex_table() %>%
  flextable::autofit()
```




# Eligible and Not Enrolled - One record per patient, per intervention phase
```{r}
#| echo: false
#| eval: true
#| 
mod_data %>%
  filter(EE == 0) %>%
  group_by(Arb_PersonId, Intervention) %>%
  arrange(EncounterDate) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(Race_Ethnicity = fct_na_value_to_level(Race_Ethnicity, level = "Unknown")) %>%
  select(Age, Sex, Race_Ethnicity, Intervention, Weight_bl, Weight_dv, BMI) %>%
  tbl_summary(by = Intervention,
              missing = "ifany",
              statistic = list(all_continuous() ~ c("{mean} ({sd})")),
              label = list(Race_Ethnicity ~ "Race/Ethnicity")) %>%
  add_overall() %>%
  as_flex_table() %>%
  flextable::autofit()

```



# Candidate Model
Variables
- Intervention (renamed to Phase), numerical binary 
- EE, numerical binary
- Weight_dv, numeric continuous, kgs. Taken from encounter
- Age_cat, character categorical. Captured from index visit in each phase
  - Where to capture index visit in intervention phase?
- Sex, character categorical, captured from control phase index visit.
- Year_at_ind, categorical, captured at the index visit in each phase
- Weight_bl, numeric continuous, baseline weight, captured at the index visit in each phase
- N_days_post_id, numeric discrete, number of days between the encounter and the participants index visit
- N_days_post_180, numeric discrete, number of days between the encounter and the 180day/6month time point of the index visit
```{r}
# Make modifications to the names and values of the phase variables so that
# the output of the lm() summary is not so cumbersome to read
mod_data %<>%
  mutate(Phase = Intervention) %>%
  mutate(Phase = case_match(Phase, 
                        "Control" ~ 0,
                        "Intervention" ~ 1))

# Create Slope* variables
mod_data %<>%
  mutate(slope1 = EE*Phase,        # EE group in intervention
         slope2 = EE*(1-Phase),    # EE group in control
         slope3 = (1-EE)*Phase,    # ENE group in intervention
         slope4 = (1-EE)*(1-Phase))# ENE group in control

```


```{r}
# Models 4 slopes
m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl + EE*Phase +
          
          # 1 - Three-way interactions
          slope1:N_days_post_id + slope1:N_days_post_180 + 
          
          # 2 - 
          slope2:N_days_post_id + slope2:N_days_post_180 + 
          
          # 3 - 
          slope3:N_days_post_id + slope3:N_days_post_180 + 
          
          # 4 - 
          slope4:N_days_post_id + slope4:N_days_post_180,
          
        # Input data frame
        data=mod_data)

broom::tidy(m) %>% 
  print(n = 31)
    
broom::glance(m) %>% print(width = Inf)
# generate_model_plot(mod_data, m)

```

<!-- ### VIF -->
```{r, echo=FALSE, eval = FALSE}
vif(m, type = "predictor")
```


<!-- # Control EE data only -->
```{r, control ee data only}
#| echo: false
#| eval: true
#| 
control <- mod_data %>% filter(Intervention == "Control", EE == 1)

m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl +
        N_days_post_id + N_days_post_180,
        data=control)

# broom::tidy(m)
# broom::glance(m)
p_con_ee <- generate_model_plot(control, m)
```

<!-- # Intervention EE data only -->
```{r, intervention ee data only}
#| echo: false
#| eval: true
intervention <- mod_data %>% filter(Intervention == "Intervention", EE == 1)

m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl +
        N_days_post_id + N_days_post_180,
        data=intervention)

p_int_ee <- generate_model_plot(intervention, m)
```

<!-- # Control ENE data only -->
```{r, control ene data only}
#| echo: false
#| eval: true
control_ene <- mod_data %>% filter(Intervention == "Control", EE != 1)

control_ene %<>%
  mutate(Year_at_ind = factor(Year_at_ind)) #Trying to relevel the data

m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl +
        N_days_post_id + N_days_post_180,
        data=control_ene)

p_con_ene <- generate_model_plot(control_ene, m)
```


<!-- # Intervention ENE data only -->
```{r, intervention ene data only}
#| echo: false
#| eval: true
#| 
intervention_ene <- mod_data %>% filter(Intervention == "Intervention", EE != 1)

m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl +
        N_days_post_id + N_days_post_180,
        data=intervention_ene)

p_int_ene <- generate_model_plot(intervention_ene, m)
```



```{r, echo=F}
ylimits <- c(104,108)
p_con_ee <- p_con_ee + ylim(ylimits) + ggtitle("Control EE")
p_int_ee <- p_int_ee + ylim(ylimits) + ggtitle("Intervention EE")

ylimits_ene <- c(86,87.5)
p_con_ene <- p_con_ene + ylim(ylimits_ene) + ggtitle("Control ENE")
p_int_ene <- p_int_ene + ylim(ylimits_ene) + ggtitle("Intervention ENE")

ggpubr::ggarrange(p_con_ee, p_int_ee, p_con_ene, p_int_ene,
                  common.legend = TRUE, legend = "bottom")
```



# Proposal Aim 1 Model with EE and ENE data
```{r}
m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl +
        N_days_post_id + N_days_post_180 + 
        Intervention + Intervention * N_days_post_id + Intervention * N_days_post_180,
        data=mod_data)

broom::tidy(m)
broom::glance(m)
# generate_model_plot(mod_data, m)
```

```{r}
#| echo: false
#| eval: true
control <- mod_data %>% filter(Intervention == "Control")

m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl +
        N_days_post_id + N_days_post_180,
        data=control)

# broom::tidy(m)
# broom::glance(m)
p_con <- generate_model_plot(control, m)
```

```{r}
#| echo: false
#| eval: true
intervention <- mod_data %>% filter(Intervention == "Intervention")

m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl +
        N_days_post_id + N_days_post_180,
        data=intervention)

# broom::tidy(m)
# broom::glance(m)
p_int <- generate_model_plot(intervention, m)
```

```{r, echo=F}
ylimits <- c(89.4,91.5)
p_con <- p_con + ylim(ylimits) + 
          ggtitle("Control")
p_int <- p_int + ylim(ylimits) + 
          ggtitle("Intervention")


ggpubr::ggarrange(p_con, p_int,
                  common.legend = TRUE, legend = "bottom")
```

```{r}

```

