---
title: "PATHWEIGH 2.0 Proposal"
format: 
  docx:
    reference-doc: "D:/PATHWEIGH/custom-reference-doc.docx"

execute: 
  echo: false
---

```{r}
#| echo: false
# library(tidyverse)
# library(gtsummary)
# library(here)
pacman::p_load(tidyverse,
               gtsummary,
               here,
               install = FALSE)
  

# Load visits_post_id
#load("S:/FM/PATHWEIGH/Quantitative/Projects/dataset_20240326/data/processed_visits_post_id_20240326.RData")
load(here("delivery_20240326/data/processed_visits_post_id_20240326.RData"))
```

```{r}
# Filter to only eligible and enrolled encounters in the intervention phase
# 260,440 unique observations in intervention
visits_post_id <- 
visits_post_id %>%
  filter(EE == 1,
         Intervention.factor == "Intervention")
```

```{r}
# Filter encounter to the period between 03-17-2023 and 03-16-2024
visits_post_id <- 
visits_post_id %>%
  filter(EncounterDate >= "2023-03-17", EncounterDate <= "2024-03-16")
```

### The total number of PATHWEIGH visits in the intervention phase from 2023-03-17 to 2024-03-16
- Denominator includes all visits from eligible and enrolled patients from the same time frame
```{r}
#| eval: false
visits_post_id %>% 
  nrow()
```

```{r}
visits_post_id %>%
  select(PW_Visit) %>%
  tbl_summary()
```

### The total number of unique PATHWEIGH patients in the intervention phase 2023-03-17 to 2024-03-16
- Denominator includes all eligible and enrolled patients from the same time frame
```{r}
#| eval: false
# unique patients in the period
visits_post_id %>%
  select(Arb_PersonId) %>%
  distinct() %>%
  nrow()
```

```{r}
pw_ids <- visits_post_id %>%
  filter(PW_Visit == 1) %>%
  select(Arb_PersonId) %>%
  distinct()

visits_post_id <-
  visits_post_id %>%
  mutate(PW_Pnt = ifelse(Arb_PersonId %in% pw_ids$Arb_PersonId, 1, 0))
```

```{r}
visits_post_id %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup() %>%
  select(PW_Pnt) %>%
  tbl_summary()
```

### The number of unique providers associated with at least one PATHWEIGH visit.
```{r}
# Get the unique providers NPI that delivered any pathweigh visit
pw_providers = visits_post_id %>%
  filter(PW_Visit == 1) %>%
  select(ProviderNpi) %>%
  distinct()
```

```{r}
# Create an indicator column of pcps that delivered pathweigh visits
visits_post_id <- 
  visits_post_id %>%
  mutate(PW_PCP = ifelse(ProviderNpi %in% pw_providers$ProviderNpi, 1, 0))
```

```{r}
# proportion of providers that delivered pw visits
visits_post_id %>%
  filter(Intervention.factor == "Intervention") %>%
  group_by(ProviderNpi) %>%
  slice_head() %>%
  ungroup() %>%
  select(PW_PCP) %>%
  tbl_summary()
```

```{r}
# create a month and year column
visits_post_id <- 
visits_post_id %>%
  mutate(year = lubridate::year(EncounterDate),
         month = lubridate::month(EncounterDate),
         yr_month = substr(EncounterDate, 0, 7))
```

### The number and percent of PW providers in each month from 2023-03-17 through 2024-03-16
```{r}
visits_post_id %>%
  group_by(yr_month, ProviderNpi) %>%
  arrange(desc(PW_PCP)) %>%
  slice_head() %>%
  group_by(yr_month) %>%
  summarise(n_pw_pcp = sum(PW_PCP)) %>%
  mutate(tot_pw_pcp = n_distinct(pw_providers$ProviderNpi),
         percent = str_c(round(100 * (n_pw_pcp/tot_pw_pcp), 2), "%")) %>%
  gt::gt()
```

```{r}
#| eval: false
#| echo: false
# How many cohorts are associated with each PW pcp
# PCPs have visits any where between 1 and 3 cohort
visits_post_id %>%
  filter(PW_PCP == 1) %>%
  group_by(ProviderNpi) %>%
  summarise(n_uniq_cohorts = n_distinct(Cohort)) %>%
  arrange(desc(n_uniq_cohorts)) %>%
  select(n_uniq_cohorts) %>%
  tbl_summary()

# what's the min date
# 2020-03-17
min(visits_post_id$EncounterDate)
max(visits_post_id$EncounterDate)  

# Assign each visits to a 6-month block
visits_post_id <- 
visits_post_id %>%
  mutate(block_6m = ifelse(EncounterDate <= "2020-09-16", "6m_01", NA)) %>%
  mutate(block_6m = ifelse(EncounterDate >= "2020-09-17" & EncounterDate <= "2021-03-16", "6m_02", block_6m),
         block_6m = ifelse(EncounterDate >= "2021-03-17" & EncounterDate <= "2021-09-16", "6m_03", block_6m),
         block_6m = ifelse(EncounterDate >= "2021-09-17" & EncounterDate <= "2022-03-16", "6m_04", block_6m),
         block_6m = ifelse(EncounterDate >= "2022-03-17" & EncounterDate <= "2022-09-16", "6m_05", block_6m),
         block_6m = ifelse(EncounterDate >= "2022-09-17" & EncounterDate <= "2023-03-16", "6m_06", block_6m),
         block_6m = ifelse(EncounterDate >= "2023-03-17" & EncounterDate <= "2023-09-16", "6m_07", block_6m),
         block_6m = ifelse(EncounterDate >= "2023-09-17" & EncounterDate <= "2024-03-16", "6m_08", block_6m),
         block_6m = ifelse(EncounterDate >= "2024-03-17", "6m_09", block_6m),
  ) 

visits_post_id %>%
  filter(PW_PCP == 1) %>%
  select(block_6m) %>%
  tbl_summary()
```

