---
title: "PATHWEIGH 2.0 Proposal"
format: 
  docx:
    reference-doc: "D:/PATHWEIGH/custom-reference-doc.docx"

execute: 
  echo: false
---

```{r}
#| echo: false
# library(tidyverse)
# library(gtsummary)
# library(here)
pacman::p_load(tidyverse,
               gtsummary,
               here,
               install = FALSE)
  

# Load visits_post_id
#load("S:/FM/PATHWEIGH/Quantitative/Projects/dataset_20240326/data/processed_visits_post_id_20240326.RData")
load(here("delivery_20240326/data/processed_visits_post_id_20240326.RData"))
```

```{r}
# Filter to only eligible and enrolled encounters in the intervention phase
# 260,440 unique observations in intervention
visits_post_id <- visits_post_id %>%
  filter(Intervention.factor == "Intervention", WPV > 0)
```

```{r}
```

### The total number of PATHWEIGH vists out of the number of discernible care for weight visits (WPVs) in the intervention phase (includes index visits)
```{r}
#| eval: false
visits_post_id %>% 
  filter(WPV > 0 ) %>%
  nrow()
```

```{r}
visits_post_id %>%
  select(PW_Visit) %>%
  tbl_summary()
```

### The total number of unique PATHWEIGH patients in the intervention out of the total number of unique patients with a discenible care for weight visit
```{r}
#| eval: false
# total number unique patients from the visits
visits_post_id %>%
  select(Arb_PersonId) %>%
  distinct() %>%
  nrow()
```

```{r}
# Get the unique patient ids of patients that had a PW_Visit
pw_ids <- visits_post_id %>%
  filter(PW_Visit == 1) %>%
  select(Arb_PersonId) %>%
  distinct()

# Create a binary indicator for patients that had a PW_Visit
visits_post_id <-
  visits_post_id %>%
  mutate(PW_Pnt = ifelse(Arb_PersonId %in% pw_ids$Arb_PersonId, 1, 0))
```

```{r}
visits_post_id %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup() %>%
  select(PW_Pnt) %>%
  tbl_summary()
```

### The number of unique providers associated with at least one PATHWEIGH visit.
```{r}
# Get the unique providers NPI that delivered any pathweigh visit
pw_providers <- visits_post_id %>%
  filter(PW_Visit == 1) %>%
  select(ProviderNpi) %>%
  distinct()
```

```{r}
# Create an indicator column of pcps that delivered pathweigh visits
visits_post_id <- visits_post_id %>%
  mutate(PW_PCP = ifelse(ProviderNpi %in% pw_providers$ProviderNpi, 1, 0))
```

```{r}
# proportion of providers that delivered pw visits
visits_post_id %>%
  filter(Intervention.factor == "Intervention") %>%
  group_by(ProviderNpi) %>%
  slice_head() %>%
  ungroup() %>%
  select(PW_PCP) %>%
  tbl_summary()
```

### Maintenance by provider

```{r}
# Convert WPV to binary to count the number of WPVs by provider
visits_post_id <- visits_post_id %>%
  mutate(WPV = ifelse(WPV > 0, 1, 0))
```

```{r}
visits_post_id %>%
  filter(ProviderNpi %in% pw_providers$ProviderNpi) %>%
  group_by(ProviderNpi) %>%
  summarise(n_wpvs = sum(WPV),
            n_pw_visits = sum(PW_Visit)) %>%
  mutate(prop_pw_visits = (n_pw_visits / n_wpvs) * 100) %>%
  mutate(cut_prop_pw = cut(prop_pw_visits, breaks = 10 * 0:10)) %>%
  select(cut_prop_pw) %>%
  tbl_summary() %>%
  as_gt()
```