---
title: "Linear Mixed Effect Models"
format:
  html:
    toc: true
    embed-resources: true
    # grid:
    #   sidebar-width: 0px
    #   body-width: 2000px
    #   margin-width: 0px
    #   gutter-width: 1.5rem
editor: source
---

```{r}

```

```{r, load packages}
#| echo: false
pacman::p_load(here,         # For managing directory paths
               magrittr,     # For the assignment pipe operator %<>%
               tidyverse,    # For data manipulation tools
               data.table,   # For reading .csv files
               openxlsx,     # For reading .xlsx files
               tictoc,       # For timing and benchmarking functions
               gtsummary,    # For tables
               DT,
               car,
               geepack,
               lme4,
               install = FALSE)


# library(tidyverse)
```

```{r}
#| echo: false

# Set the project root
proj_root <- "S:/FM/PATHWEIGH/Quantitative/Projects/"

# Set the data delivery date to the appropriate data set
# delivery <- 20231010
delivery <- 20240326

# Load generate_plot function --------------------------------------------------
# For use in linear models only, not linear mixed models
source(str_c(proj_root, "emr_data_processing/subscripts/generate_model_plots.R"))

# Load full model data ---------------------------------------------------------
load(str_c(proj_root, "dataset_", delivery, "/data/mod_data_full_", delivery, ".Rdata"))

# mod_data output is all data available, but there are cases when only 18mo data
# is required, make a backup
mod_data_full <- mod_data

# Filter mod data to 18 months
mod_data %<>%
  filter(N_months_post_id <= 18)

# Load ee model data -----------------------------------------------------------
load(str_c(proj_root, "dataset_", delivery, "/data/mod_data_ee_", delivery, ".Rdata"))

# Filter ee data to 18 months
ee %<>%
  filter(N_months_post_id <= 18)
```

# Model variables for mod_data data with EE and ENE patients
Variables
- Intervention (renamed to Phase), numerical binary 
- EE, numerical binary
- Weight_dv, numeric continuous, kgs. Taken from encounter
- Age_cat, character categorical. Captured from index visit in each phase
  - Where to capture index visit in intervention phase?
- Sex, character categorical, captured from Intervention phase index visit.
- Year_at_ind, categorical, captured at the index visit in each phase
- Weight_bl, numeric continuous, baseline weight, captured at the index visit in each phase
- N_days_post_id, numeric discrete, number of days between the encounter and the participants index visit
- N_days_post_180, numeric discrete, number of days between the encounter and the 180day/6month time point of the index visit
```{r}


# Make modifications to the names and values of the phase variables so that
# the output of the lm() summary is not so cumbersome to read
# n.b. these modifications are implemented in 02_process_rdata_image script
# but place here for reference
# mod_data %<>%
#   mutate(Phase = Intervention) %>%
#   mutate(Phase = case_match(Phase, 
#                         "Control" ~ 0,
#                         "Intervention" ~ 1))
# mod_data %<>%
#   mutate(slope1 = EE*Phase,        # EE group in intervention
#          slope2 = EE*(1-Phase),    # EE group in control
#          slope3 = (1-EE)*Phase,    # ENE group in intervention
#          slope4 = (1-EE)*(1-Phase))# ENE group in control
```

# Data elements in mod_data object
```{r}
str(mod_data)
```



# Piecewise lm() EE + ENE
```{r, eval = FALSE}
# Models 4 slopes
m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl + EE + Phase +
          
          # 1 - Three-way interactions
          slope1:N_days_post_id + slope1:N_days_post_180 + 
          
          # 2 - 
          slope2:N_days_post_id + slope2:N_days_post_180 + 
          
          # 3 - 
          slope3:N_days_post_id + slope3:N_days_post_180 + 
          
          # 4 - 
          slope4:N_days_post_id + slope4:N_days_post_180,
          
        # Input data frame
        data=mod_data)

broom::tidy(m) %>% 
  print(n = 31)
    
broom::glance(m) %>% print(width = Inf)
# generate_model_plot(mod_data, m)

```

<!-- # Control EE data only -->
```{r, control ee data only}
control <- mod_data %>% filter(Intervention == "Control", EE == 1)

m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl +
        N_days_post_id + N_days_post_180,
        data=control)

# broom::tidy(m)
# broom::glance(m)
p_con_ee <- generate_model_plot(control, m)
```

<!-- # Intervention EE data only -->
```{r, intervention ee data only}
#| warning: false  

intervention <- mod_data %>% filter(Intervention == "Intervention", EE == 1)

m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl +
        N_days_post_id + N_days_post_180,
        data=intervention)

p_int_ee <- generate_model_plot(intervention, m)
```

<!-- # Control ENE data only -->
```{r, control ene data only}
#| warning: false  

control_ene <- mod_data %>% filter(Intervention == "Control", EE != 1)

control_ene %<>%
  mutate(Year_at_ind = factor(Year_at_ind)) #Trying to relevel the data

m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl +
        N_days_post_id + N_days_post_180,
        data=control_ene)

p_con_ene <- generate_model_plot(control_ene, m)
```

<!-- # Intervention ENE data only -->
```{r, intervention ene data only}
#| warning: false  

intervention_ene <- mod_data %>% filter(Intervention == "Intervention", EE != 1)

m <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl +
        N_days_post_id + N_days_post_180,
        data=intervention_ene)

p_int_ene <- generate_model_plot(intervention_ene, m)
```

```{r, echo=F}
#| warning: false  

# Set the ylimits based on the data delivery date
if (delivery == "20240326"){
  ylimits <-  c(102,108)
  ylimits_ene <- c(85,87.5)

} else if (delivery == "20231010"){
    ylimits <- c(104,108)
    ylimits_ene <- c(86,87.5)
}

# Create sub plots for EE
p_con_ee <- p_con_ee + ylim(ylimits) + ggtitle("Control EE")
p_int_ee <- p_int_ee + ylim(ylimits) + ggtitle("Intervention EE")

# Create sub plots for ENE
p_con_ene <- p_con_ene + ylim(ylimits_ene) + ggtitle("Control ENE")
p_int_ene <- p_int_ene + ylim(ylimits_ene) + ggtitle("Intervention ENE")

# Arrange EE and ENE sub plots into one figure
ggpubr::ggarrange(p_con_ee, p_int_ee, p_con_ene, p_int_ene,
                  common.legend = TRUE, legend = "bottom")
```

# Piecewise lm() EE only
```{r}
lm_mod <- lm(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl + slope1 + 
          # 1 -
          slope1:N_days_post_id + slope1:N_days_post_180 + 
          
          # 2 - 
          slope2:N_days_post_id + slope2:N_days_post_180,
                
          # Input data frame
          data=ee)

broom::tidy(lm_mod)
```

# lmer() with EE only, categorical values
```{r}
# LMER clustered on department external name and patient id
lmer_mod <- lmer(Weight_dv ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl + slope1 +
          # 1 -
          slope1:N_days_post_id + slope1:N_days_post_180 + 
          
          # 2 - 
          slope2:N_days_post_id + slope2:N_days_post_180 + 
          
          # Random effects, dept name causes convergence warnings   
          # (1| DepartmentExternalName) + (1| Arb_PersonId),
          (1| Arb_PersonId),
                
          # Input data frame
          data=ee)
 
broom.mixed::tidy(lmer_mod)
```

```{r}
predicted_vals <- predict(lmer_mod, ee, re.form=NA, type="response")

# Create a data set of the predicted values and categorical lmer data input
lmer_cat_data <- bind_cols(ee, predicted_vals) %>%
  rename(predicted = `...115`,
         observed = Weight_kgs)

# Plot data
# To plot the predicted and average values, first select the columns of interest,
# then group data by Phase and the number of months after index visit,
# then calculate means, drop the grouping, and recode the Phase values to be 
# able to display a faceted plot.
# Next, convert the data to long and plot 
lmer_cat_data %>%  
  select(Phase, N_months_post_id, observed, predicted) %>%
  group_by(Phase, N_months_post_id) %>%
  summarise(across(observed:predicted, ~ mean(.x, rm.na = TRUE)), .groups = "drop") %>%
  mutate(Phase = case_match(Phase, 0 ~ "Control",
                            1 ~ "Intervention")) %>%
  pivot_longer(cols = observed:predicted, names_to = "Type", values_to = "Avg_Weight_kgs") %>%
  ggplot(., aes(x = N_months_post_id, y = Avg_Weight_kgs, color = Type)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Phase) +
  theme_minimal()
```

```{r}
# Count the sample size for each month after index and phase 
lmer_cat_data %>%
  select(Phase, N_months_post_id, observed, predicted) %>%
  group_by(Phase, N_months_post_id) %>%
  count() %>%
  mutate(N_days_post_id = N_months_post_id * 30)
```



# lmer() with EE only, binary variables dataset
```{r}
# Convert all categorical variables to sets of binary variables
ee_bin <- 
  ee %>% 
  mutate(age_lt_45 = ifelse(Age_cat == "<=45", 1, 0),
         age_45_to_60 = ifelse(Age_cat == "45-60", 1, 0),
         age_gt_60 = ifelse(Age_cat == ">60", 1, 0),
         sex_m = ifelse(Sex == "Male", 1, 0),
         sex_f = ifelse(Sex == "Female", 1, 0),
         reth_nhw = ifelse(Race_Ethnicity == "Non-Hispanic White", 1, 0),
         reth_his = ifelse(Race_Ethnicity == "Hispanic or Latino", 1, 0),
         reth_blk = ifelse(Race_Ethnicity == "Black or African American", 1, 0),
         reth_asn = ifelse(Race_Ethnicity == "Asian", 1, 0),
         reth_oth = ifelse(Race_Ethnicity == "Other", 1, 0),
         reth_ukn = ifelse(Race_Ethnicity == "Unknown", 1, 0),
         year_at_ind0 = ifelse(Year_at_ind == "Year0", 1, 0),
         year_at_ind1 = ifelse(Year_at_ind == "Year1", 1, 0),
         year_at_ind2 = ifelse(Year_at_ind == "Year2", 1, 0),
         year_at_ind3 = ifelse(Year_at_ind == "Year3", 1, 0))
```


```{r}
# Linear mixed model with binary variables
lmer_mod_bin <- lmer(Weight_dv ~ 
                   
          # age
          age_45_to_60 + age_gt_60 + 
           
          # sex
          sex_m + 
          
          # race ethnicity
          reth_his + reth_blk + reth_asn + reth_oth + reth_ukn + 
           
          # year at index
          year_at_ind1 + year_at_ind2 + year_at_ind3 + 
           
          # Weight at baseline
          Weight_bl + slope1 +
             
          # 1 - control phase
          slope1:N_days_post_id + slope1:N_days_post_180 + 
          
          # 2 - intervention phase
          slope2:N_days_post_id + slope2:N_days_post_180 + 
          
          # Clustering, convergence issues with both dept and personid   
          # (1| DepartmentExternalName) + (1| Arb_PersonId),
          (1| Arb_PersonId),
                
          # Input data frame
          data=ee_bin
          
          # Set REML
          # REML = TRUE
          
          # control = lmerControl(optimizer = "nloptwrap", optCtrl = list(algorithm = "NLOPT_LN_NELDERMEAD"))
          )


broom.mixed::tidy(lmer_mod) %>%
  print(n = 81)
```

## Average dataset for predictions
### Control
```{r}
# Convert PHQ2:GAD7 to numeric, to be able to use the summarise_all() function
ee_bin %<>%
  mutate(across(PHQ2:GAD7, ~ as.numeric(.x)))

# Create a subset of control phase data from the binary data set
ee_con <- ee_bin %>% filter(Phase == 0)

# Create a sequence
# 18 * 30 = 540
N_days_post_id <- seq(0, 540, by = 30)

# Convert vector to data frame consisting of 0-18 months in control
avg_data_con <- data.frame(N_days_post_id)

# Create a vector of number of days after 180 days (6 months)
avg_data_con$N_days_post_180 <- c(rep(0, 7),seq(30, 360, by = 30))

# Calculate all means in control phase data
means_con <- ee_con %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup() %>%
  select(Phase:slope2, 
         Weight_bl,
         age_lt_45:year_at_ind3) %>%
  summarise_all(list(mean))

# Create control data subset
avg_data_con %<>%
  mutate(age_45_to_60 = means_con$age_45_to_60,
         age_gt_60 = means_con$age_gt_60,
         sex_m = means_con$sex_m,
         reth_his = means_con$reth_his,
         reth_blk = means_con$reth_blk,
         reth_asn = means_con$reth_asn,
         reth_oth = means_con$reth_oth,
         reth_ukn = means_con$reth_ukn,
         year_at_ind1 = means_con$year_at_ind1,
         year_at_ind2 = means_con$year_at_ind2,
         year_at_ind3 = means_con$year_at_ind3,     
         Weight_bl = means_con$Weight_bl,
         Phase = 0,
         slope1 = 0,
         slope2 = 1)

# How many patients used for each month average
avg_data_con_n <- ee_con %>%
  group_by(N_months_post_id)%>%
  count()%>%
  ungroup() %>%
  mutate(N_days_post_id = N_months_post_id * 30) %>%
  select(-N_months_post_id)

avg_data_con %<>%
  left_join(., avg_data_con_n, by = "N_days_post_id")
```

### Intervention
```{r}
# Create a subset of intervention phase data
ee_int <- ee_bin %>% filter(Phase == 1)

# 18 months worth of n_days
# 18 * 30 = 540
N_days_post_id <- seq(0, 540, by = 30)

# Convert vector to data frame
avg_data_int <- data.frame(N_days_post_id)

# Create a vector of number of days after 180 days (6 months)
avg_data_int$N_days_post_180 <- c(rep(0, 7),seq(30, 360, by = 30))

# Calculate all means in control phase data
means_int <- ee_int %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup() %>%
  select(Phase:slope2, 
         Weight_bl,
         age_lt_45:year_at_ind3) %>%
  summarise_all(list(mean))

# Create control data subset
avg_data_int %<>%
  mutate(age_45_to_60 = means_int$age_45_to_60,
         age_gt_60 = means_int$age_gt_60,
         sex_m = means_int$sex_m,
         reth_his = means_int$reth_his,
         reth_blk = means_int$reth_blk,
         reth_asn = means_int$reth_asn,
         reth_oth = means_int$reth_oth,
         reth_ukn = means_int$reth_ukn,
         year_at_ind1 = means_int$year_at_ind1,
         year_at_ind2 = means_int$year_at_ind2,
         year_at_ind3 = means_int$year_at_ind3,     
         Weight_bl = means_int$Weight_bl,
         Phase = 1,
         slope1 = 1,
         slope2 = 0)

# How many patients used for each month average
avg_data_int_n <- ee_int %>%
  group_by(N_months_post_id)%>%
  count()%>%
  ungroup() %>%
  mutate(N_days_post_id = N_months_post_id * 30) %>%
  select(-N_months_post_id)

avg_data_int %<>%
  left_join(., avg_data_int_n, by = "N_days_post_id")
```

### Bind control and intervention
```{r}
avg_data <- bind_rows(avg_data_con, avg_data_int)

# write_csv(avg_data, file = here("avg_data.csv"))
```

### Plot observed values
```{r}
# First average across each weight_dv in each month per phase
observed <-
  ee %>%
    select(Arb_PersonId, Weight_dv, N_months_post_id, Phase) %>%
    group_by(Arb_PersonId, N_months_post_id, Phase) %>%
    summarise(Weight_dv = mean(Weight_dv),
              .groups = "drop") %>%
    group_by(N_months_post_id, Phase) %>%
    summarize(Avg_Weight_kgs = mean(Weight_dv),
              .groups = "drop") %>%
  mutate(Type = "Observed")

# observed %>%
#   filter(N_months_post_id <= 18) %>%
#   ggplot(., aes(x = N_months_post_id, y = Avg_Weight_kgs)) +
#   geom_line() +
#   facet_wrap(~Phase)
```

### Predicted values, predict()
```{r}
predicted_vals <- predict(lmer_mod_bin, avg_data, re.form=NA, type="response")

avg_data$predicted_vals <- predicted_vals

predicted <- 
  avg_data %>%
  mutate(Avg_Weight_kgs = predicted_vals,
         Type = "Predicted",
         N_months_post_id = round(N_days_post_id/30)) %>%
  select(N_months_post_id, Phase, Avg_Weight_kgs, Type)
```


### Bind rows and plot lmer with the average person
```{r}
bind_rows(observed, predicted) %>%
  filter(N_months_post_id <= 18) %>%
  mutate(Phase = case_match(Phase, 0 ~ "Control",
                            1 ~ "Intervention")) %>%
  ggplot(., aes(x = N_months_post_id, y = Avg_Weight_kgs, color = Type)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Phase) +
  theme_minimal()
```
## Average dataset for predictions do not slice head
### Control
```{r}
# Create a subset of control phase data from the binary data set
ee_con <- ee_bin %>% filter(Phase == 0)

# Create a sequence
# 18 * 30 = 540
N_days_post_id <- seq(0, 540, by = 30)

# Convert vector to data frame consisting of 0-18 months in control
avg_data_con <- data.frame(N_days_post_id)

# Create a vector of number of days after 180 days (6 months)
avg_data_con$N_days_post_180 <- c(rep(0, 7),seq(30, 360, by = 30))

# Calculate all means in control phase data
means_con <- ee_con %>%
  # group_by(Arb_PersonId) %>%
  # slice_head() %>%
  # ungroup() %>%
  select(Phase:slope2, 
         Weight_bl,
         age_lt_45:year_at_ind3) %>%
  summarise_all(list(mean))

# Create control data subset
avg_data_con %<>%
  mutate(age_45_to_60 = means_con$age_45_to_60,
         age_gt_60 = means_con$age_gt_60,
         sex_m = means_con$sex_m,
         reth_his = means_con$reth_his,
         reth_blk = means_con$reth_blk,
         reth_asn = means_con$reth_asn,
         reth_oth = means_con$reth_oth,
         reth_ukn = means_con$reth_ukn,
         year_at_ind1 = means_con$year_at_ind1,
         year_at_ind2 = means_con$year_at_ind2,
         year_at_ind3 = means_con$year_at_ind3,     
         Weight_bl = means_con$Weight_bl,
         Phase = 0,
         slope1 = 0,
         slope2 = 1)

# How many patients used for each month average
avg_data_con_n <- ee_con %>%
  group_by(N_months_post_id)%>%
  count()%>%
  ungroup() %>%
  mutate(N_days_post_id = N_months_post_id * 30) %>%
  select(-N_months_post_id)

avg_data_con %<>%
  left_join(., avg_data_con_n, by = "N_days_post_id")
```

### Intervention
```{r}
# Create a subset of intervention phase data
ee_int <- ee_bin %>% filter(Phase == 1)

# 18 months worth of n_days
# 18 * 30 = 540
N_days_post_id <- seq(0, 540, by = 30)

# Convert vector to data frame
avg_data_int <- data.frame(N_days_post_id)

# Create a vector of number of days after 180 days (6 months)
avg_data_int$N_days_post_180 <- c(rep(0, 7),seq(30, 360, by = 30))

# Calculate all means in control phase data
means_int <- ee_int %>%
  # group_by(Arb_PersonId) %>%
  # slice_head() %>%
  # ungroup() %>%
  select(Phase:slope2, 
         Weight_bl,
         age_lt_45:year_at_ind3) %>%
  summarise_all(list(mean))

# Create control data subset
avg_data_int %<>%
  mutate(age_45_to_60 = means_int$age_45_to_60,
         age_gt_60 = means_int$age_gt_60,
         sex_m = means_int$sex_m,
         reth_his = means_int$reth_his,
         reth_blk = means_int$reth_blk,
         reth_asn = means_int$reth_asn,
         reth_oth = means_int$reth_oth,
         reth_ukn = means_int$reth_ukn,
         year_at_ind1 = means_int$year_at_ind1,
         year_at_ind2 = means_int$year_at_ind2,
         year_at_ind3 = means_int$year_at_ind3,     
         Weight_bl = means_int$Weight_bl,
         Phase = 1,
         slope1 = 1,
         slope2 = 0)

# How many patients used for each month average
avg_data_int_n <- ee_int %>%
  group_by(N_months_post_id)%>%
  count()%>%
  ungroup() %>%
  mutate(N_days_post_id = N_months_post_id * 30) %>%
  select(-N_months_post_id)

avg_data_int %<>%
  left_join(., avg_data_int_n, by = "N_days_post_id")
```

### Bind control and intervention
```{r}
avg_data <- bind_rows(avg_data_con, avg_data_int)
```


### Predicted values, predict()
```{r}
predicted_vals <- predict(lmer_mod_bin, avg_data, re.form=NA, type="response")

avg_data$predicted_vals <- predicted_vals

predicted <- 
  avg_data %>%
  mutate(Avg_Weight_kgs = predicted_vals,
         Type = "Predicted",
         N_months_post_id = round(N_days_post_id/30)) %>%
  select(N_months_post_id, Phase, Avg_Weight_kgs, Type)
```


### Bind rows and plot lmer with the average person
```{r}
bind_rows(observed, predicted) %>%
  filter(N_months_post_id <= 18) %>%
  mutate(Phase = case_match(Phase, 0 ~ "Control",
                            1 ~ "Intervention")) %>%
  ggplot(., aes(x = N_months_post_id, y = Avg_Weight_kgs, color = Type)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Phase) +
  theme_minimal()
```


### Average values for those with 18 month to compare with average_data
```{r}
# Calculate all means in control phase data
means_con_18m <- ee_con %>%
  filter(Phase == 0, N_months_post_id == 18) %>%
  select(all_of(names(avg_data)), Arb_PersonId) %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup() %>%
  select(-Arb_PersonId) %>%
  summarise_all(list(mean)) 
  
means_int_18m <- ee_int %>%
  filter(Phase == 1, N_months_post_id == 18) %>%
  select(all_of(names(avg_data)), Arb_PersonId) %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup() %>%
  select(-Arb_PersonId) %>%
  summarise_all(list(mean)) 

output <- bind_rows(means_con_18m,
          means_int_18m,
          (avg_data %>%
  filter(N_days_post_id == 540)))

write_csv(output, file = here("18m_means.csv"))
```


### Confidence intervals for coefficients
```{r}
confint(lmer_mod)
```

### Predicted values, predictInterval()
```{r}
# Add a variable for the random effect which is required for predictInterval()
# Will result in warning since these levels are not represented in the model, 
# but are not ot interest, only the fixed coefficients.
avg_data %<>%
  mutate(Arb_PersonId = seq(1,38))

predicted_intervals <- 
  merTools::predictInterval(lmer_mod,
                which = "fixed",
                newdata = avg_data,
                n.sims = 1000)
```

```{r}
# Plot the observed values, predicted values, and the confidence interval values
intervals <- bind_cols(avg_data, predicted_intervals) %>%
  mutate(N_months_post_id = round(N_days_post_id/30)) %>%
  dplyr::select(N_months_post_id, Phase, fit, lwr, upr) %>%
  pivot_longer(., cols = fit:upr, values_to = "Avg_Weight_kgs", names_to = "Type") %>%
  dplyr::select(N_months_post_id, Phase, Avg_Weight_kgs, Type)
    


bind_rows(observed, predicted, intervals) %>%
  filter(N_months_post_id <= 18,
         Type != "Predicted") %>% #filtering our fit values to plot predicted instead
  mutate(Phase = case_match(Phase, 0 ~ "Control",
                            1 ~ "Intervention"),
         Type = ifelse(Type == "fit", "Predicted", Type),
         Type = factor(Type, levels = c("Observed", "lwr", "Predicted", "upr"))) %>%
  ggplot(., aes(x = N_months_post_id, y = Avg_Weight_kgs, color = Type)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Phase) +
  theme_minimal()
```

```{r}
boot_ci <- bootMer(lmer_mod,
                   nsim = 100,
                   FUN = function(x) { predict(x, newdata = avg_data, re.form = NA) })
 
boot_ci
```

```{r}
# Get average Independent variables
# Control
# Age_cat
ee %>%
  filter(Phase == 0) %>%
  select(Age_cat) %>%
  tbl_summary()

# Sex
ee %>%
  filter(Phase == 0) %>%
  select(Sex) %>%
  tbl_summary()

# Race_ethnicity
ee %>%
  filter(Phase == 0) %>%
  select(Race_Ethnicity) %>%
  tbl_summary()

# Year_at_ind
ee %>%
  filter(Phase == 0) %>%
  select(Year_at_ind) %>%
  tbl_summary()

# Weigh_bl
ee %>%
  filter(Phase == 0) %>%
  select(Weight_bl) %>%
  tbl_summary(statistic = list(all_continuous() ~ "{mean}"))
```

# Plot predictions on all observed data with model binary
```{r}
predicted_vals <- predict(lmer_mod_bin, ee_bin, re.form=NA, type="response")

# Create a data set of the predicted values and categorical lmer data input
lmer_bin_data <- bind_cols(ee_bin, predicted_vals) %>%
  rename(predicted = `...130`,
         observed = Weight_kgs)

# Plot data
# To plot the predicted and average values, first select the columns of interest,
# then group data by Phase and the number of months after index visit,
# then calculate means, drop the grouping, and recode the Phase values to be 
# able to display a faceted plot.
# Next, convert the data to long and plot 
lmer_bin_data %>%  
  select(Phase, N_months_post_id, observed, predicted) %>%
  group_by(Phase, N_months_post_id) %>%
  summarise(across(observed:predicted, ~ mean(.x, rm.na = TRUE)), .groups = "drop") %>%
  mutate(Phase = case_match(Phase, 0 ~ "Control",
                            1 ~ "Intervention")) %>%
  pivot_longer(cols = observed:predicted, names_to = "Type", values_to = "Avg_Weight_kgs") %>%
  ggplot(., aes(x = N_months_post_id, y = Avg_Weight_kgs, color = Type)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Phase) +
  theme_minimal()
```



# GEE Model
```{r}
# Sort all observations within patient and arrange by months after index visit
gee_data <- ee %>%
  group_by(Arb_PersonId) %>%
  arrange(N_days_post_id) %>%
  ungroup()

gee_mod <- geeglm(Weight_dv ~ 
                   
          # age
          age_45_to_60 + age_gt_60 + 
           
          # sex
          sex_m + 
          
          # race ethnicity
          reth_his + reth_blk + reth_asn + reth_oth + reth_ukn + 
           
          # year at index
          year_at_ind1 + year_at_ind2 + year_at_ind3 + 
           
          # Weight at baseline
          Weight_bl + slope1 +
             
          # 1 - control phase
          slope1:N_days_post_id + slope1:N_days_post_180 + 
          
          # 2 - intervention phase
          slope2:N_days_post_id + slope2:N_days_post_180, 
          
          # Clustering variable 
          id = Arb_PersonId,
                
          # Input data frame
          data=gee_data)
          
broom::tidy(gee_mod)
```

## Average dataset for predictions
```{r}
# Recreate the average data set
avg_data <- bind_rows(avg_data_con, avg_data_int)

# Create
predicted_vals <- predict(gee_mod, avg_data, re.form=NA, type="response")

avg_data$predicted_vals <- predicted_vals

predicted <- 
  avg_data %>%
  mutate(Avg_Weight_kgs = predicted_vals,
         Type = "Predicted",
         N_months_post_id = round(N_days_post_id/30)) %>%
  select(N_months_post_id, Phase, Avg_Weight_kgs, Type)
```


### Bind rows and plot
```{r}
bind_rows(observed, predicted) %>%
  filter(N_months_post_id <= 18) %>%
  mutate(Phase = case_match(Phase, 0 ~ "Control",
                            1 ~ "Intervention")) %>%
  ggplot(., aes(x = N_months_post_id, y = Avg_Weight_kgs, color = Type)) +
  geom_line() +
  geom_point() +
  facet_wrap(~Phase) +
  theme_minimal()
```


# Distribution of individuals with weight within +/- 30 days of 6mo, 12mo, and 18mo
## Unique number of patients in each phase (includes patients with visits in both phases)
```{r}
# ensure that both mod_data and ee deliver the same results as long as the same
# N_months_post_id filter is implemented.
mod_data %>% 
  filter(EE == 1) %>% 
  group_by(Arb_PersonId, Intervention) %>% 
  slice_head() %>% ungroup() %>% 
  select(Intervention) %>% 
  tbl_summary()
```



```{r}
ee %>% 
  group_by(Arb_PersonId, Intervention) %>% 
  slice_head() %>% 
  ungroup() %>% 
  select(Intervention) %>% 
  tbl_summary()
```

### Frequencies (%) of patients that have weight values at 6m, 12m, or 18m with 90day windows
```{r}
# Create a new dataset where each encounter has an indicator of whether or not it falls into
# one of the 6m, 12m, or 18m windows.
win <- 90

windows <-
  mod_data %>%
  filter(EE == 1) %>%
  mutate(is_6m = ifelse(N_days_post_id >= ((6*30)-win) & N_days_post_id <= ((6*30)+win), 1, 0),
         is_12m = ifelse(N_days_post_id >= ((12*30)-win) & N_days_post_id <= ((12*30)+win), 1, 0),
         is_18m = ifelse(N_days_post_id >= ((18*30)-win) & N_days_post_id <= ((18*30)+win), 1, 0))

# Create subsets of patient ids that have encounters that fall within one of the
# specified windows in the control phase
con_6m <-
windows %>%
  filter(Intervention == "Intervention", is_6m == 1) %>%
  pull(Arb_PersonId)

con_12m <-
windows %>%
  filter(Intervention == "Intervention", is_12m == 1) %>%
  pull(Arb_PersonId)

con_18m <-
windows %>%
  filter(Intervention == "Intervention", is_18m == 1) %>%
  pull(Arb_PersonId)

control <-
  mod_data %>%
  filter(EE == 1, Intervention == "Control") %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(has_6m = ifelse(Arb_PersonId %in% con_6m, 1, 0),
         has_12m = ifelse(Arb_PersonId %in% con_12m, 1, 0),
         has_18m = ifelse(Arb_PersonId %in% con_18m, 1, 0))


# Create subsets of patient ids that have encounters that fall within one of the
# specified windows in the intervention phase
int_6m <-
windows %>%
  filter(Intervention == "Intervention", is_6m == 1) %>%
  pull(Arb_PersonId)

int_12m <-
windows %>%
  filter(Intervention == "Intervention", is_12m == 1) %>%
  pull(Arb_PersonId)

int_18m <-
windows %>%
  filter(Intervention == "Intervention", is_18m == 1) %>%
  pull(Arb_PersonId)

intervention <-
mod_data %>%
  filter(EE == 1, Intervention == "Intervention") %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(has_6m = ifelse(Arb_PersonId %in% int_6m, 1, 0),
         has_12m = ifelse(Arb_PersonId %in% int_12m, 1, 0),
         has_18m = ifelse(Arb_PersonId %in% int_18m, 1, 0))


bind_rows(control, intervention) %>%
  mutate(row_sum = has_6m + has_12m + has_18m,
         has_2_of_3 = ifelse(row_sum >= 2, 1, 0 )) %>%
  select(has_6m:has_18m, has_2_of_3, Intervention)%>%
  tbl_summary(by = Intervention)
```


### Frequencies (%) of patients that have weight values at 6m, 12m, or 18m with 90day windows except for 18 months which was extended out to any visit beyond 18 months.
```{r}
mod_data_18m <- mod_data
mod_data <- mod_data_full

# Create a new dataset where each encounter has an indicator of whether or not it falls into
# one of the 6m, 12m, or 18m windows.
win <- 90

windows <-
  mod_data %>%
  filter(EE == 1) %>%
  mutate(is_6m = ifelse(N_days_post_id >= ((6*30)-win) & N_days_post_id <= ((6*30)+win), 1, 0),
         is_12m = ifelse(N_days_post_id >= ((12*30)-win) & N_days_post_id <= ((12*30)+win), 1, 0),
         # is_18m = ifelse(N_days_post_id >= ((18*30)-win) & N_days_post_id <= ((18*30)+win), 1, 0))
         is_18m = ifelse(N_days_post_id >= ((18*30)-win), 1, 0))


# Create subsets of patient ids that have encounters that fall within one of the
# specified windows in the control phase
con_6m <-
windows %>%
  filter(Intervention == "Intervention", is_6m == 1) %>%
  pull(Arb_PersonId)

con_12m <-
windows %>%
  filter(Intervention == "Intervention", is_12m == 1) %>%
  pull(Arb_PersonId)

con_18m <-
windows %>%
  filter(Intervention == "Intervention", is_18m == 1) %>%
  pull(Arb_PersonId)

control <-
  mod_data %>%
  filter(EE == 1, Intervention == "Control") %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(has_6m = ifelse(Arb_PersonId %in% con_6m, 1, 0),
         has_12m = ifelse(Arb_PersonId %in% con_12m, 1, 0),
         has_18m = ifelse(Arb_PersonId %in% con_18m, 1, 0))


# Create subsets of patient ids that have encounters that fall within one of the
# specified windows in the intervention phase
int_6m <-
windows %>%
  filter(Intervention == "Intervention", is_6m == 1) %>%
  pull(Arb_PersonId)

int_12m <-
windows %>%
  filter(Intervention == "Intervention", is_12m == 1) %>%
  pull(Arb_PersonId)

int_18m <-
windows %>%
  filter(Intervention == "Intervention", is_18m == 1) %>%
  pull(Arb_PersonId)

intervention <-
mod_data %>%
  filter(EE == 1, Intervention == "Intervention") %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(has_6m = ifelse(Arb_PersonId %in% int_6m, 1, 0),
         has_12m = ifelse(Arb_PersonId %in% int_12m, 1, 0),
         has_18m = ifelse(Arb_PersonId %in% int_18m, 1, 0))


bind_rows(control, intervention) %>%
  mutate(row_sum = has_6m + has_12m + has_18m,
         has_2_of_3 = ifelse(row_sum >= 2, 1, 0 )) %>%
  select(has_6m:has_18m, has_2_of_3, Intervention)%>%
  tbl_summary(by = Intervention)
```

### Distribution of the last N_days_post_id at the last available visit
```{r}
mod_data_full %>%
  filter(EE == 1) %>%
  group_by(Arb_PersonId, Intervention) %>%
  arrange(desc(N_days_post_id)) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(month_of_lv = round(N_days_post_id/30)) %>%
  ggplot(., aes(x = month_of_lv)) +
  theme_minimal() +
  geom_histogram(binwidth = 1, color = "black", alpha = 0.7) +
  ylab("Count") +
  facet_wrap(~Intervention)
```

```{r}
# Create a table of frequency and percentage months since the index visit for the
# last available visit
mod_data %>%
  filter(EE == 1) %>%
  group_by(Arb_PersonId) %>%
  arrange(desc(N_days_post_id)) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(month_of_lv = round(N_days_post_id/30),
         month_of_lv = factor(month_of_lv)) %>%
  select(month_of_lv) %>%
  tbl_summary()

# same as above but by intervention
mod_data %>%
  filter(EE == 1) %>%
  group_by(Arb_PersonId) %>%
  arrange(desc(N_days_post_id)) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(month_of_lv = round(N_days_post_id/30),
         month_of_lv = factor(month_of_lv)) %>%
  select(month_of_lv, Intervention) %>%
  tbl_summary(by = Intervention)

# What is the max month of the last available visit?
mod_data %>%
  filter(EE == 1) %>%
  group_by(Arb_PersonId) %>%
  arrange(desc(N_days_post_id)) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(month_of_lv = round(N_days_post_id/30)) %>%
  pull(month_of_lv) %>%
  max(.)
  
```




# 1. Compare the subgroup of patients whose last visit is within 6m and those with last visit after 6m: compare baseline characteristics, logistic regression for indicator of last visit within 6m and check if control/intervention is significant.
```{r}
# Capture the unique Arb_PersonIds that have a last visit within 6m of index in control phase
has_6m_con <- 
ee %>%
  filter(Intervention == "Control") %>%
  group_by(Arb_PersonId) %>%
  arrange(EncounterDate) %>%
  slice_tail() %>%
  ungroup() %>%
  filter(N_days_post_id <= 180) %>%
  pull(Arb_PersonId)

# Total number of unique patients in control phase
ee %>%
  filter(Intervention == "Control") %>%
  distinct(Arb_PersonId) %>%
  nrow()
```


```{r}
# Capture the unique Arb_PersonIds that have a visit within 6m of index in int
has_6m_int <- 
ee %>%
  filter(Intervention == "Intervention") %>%
  group_by(Arb_PersonId) %>%
  arrange(EncounterDate) %>%
  slice_tail() %>%
  ungroup() %>%
  filter(N_days_post_id <= 180) %>%
  pull(Arb_PersonId)

ee %>%
  filter(Intervention == "Intervention") %>%
  distinct(Arb_PersonId) %>%
  nrow()
```


```{r}
# Create a variable that indicates which patients have visits within 6m
# slice one row per patient, since all covariates are invariant
has_6m_data <- 
ee %>%
  mutate(lv_w_in_6m = ifelse(Arb_PersonId %in% has_6m_con & Phase == 0, 1, 
                         ifelse(Arb_PersonId %in% has_6m_int & Phase == 1, 1, 0))) %>%
  group_by(Arb_PersonId, Phase) %>%
  slice_head() %>%
  ungroup()

# Table the values of the indicator variable has_6m to show who has a subsequent
# visit within 6 months
table(has_6m_data$lv_w_in_6m)

# ee when setting 60,797 rows
baseline_characteristics <- has_6m_data %>%
  select(Intervention, Race_Ethnicity, Age, Sex, Weight_kgs, Systolic_blood_pressure:N_Meds_AOM, lv_w_in_6m) %>%
  names()

has_6m_data %<>%
  mutate(PHQ2 = as.numeric(PHQ2),
         PHQ9 = as.numeric(PHQ9),
         GAD7 = as.numeric(GAD7))

has_6m_data %>%
  select(all_of(baseline_characteristics)) %>%
  mutate(lv_w_in_6m = ifelse(lv_w_in_6m == 1, "Yes", "No")) %>%
  tbl_strata(
    strata = Intervention,
    .tbl_fun = 
      ~.x %>%
      tbl_summary(by = lv_w_in_6m,
                  type = list(all_dichotomous() ~ "categorical",
                              PHQ2 ~ "continuous"),
                  statistic = all_continuous() ~ "{mean} ({sd})")
    )
```

```{r}
# Capture one row per patient
logit_mod_data <- 
  has_6m_data %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup()

# logistic regression model
summary(
  
  glm(lv_w_in_6m ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl,
    data = logit_mod_data,
    family = "binomial")
  
  )



```

```{r}
# Capture one row per patient
logit_mod_data_con <- 
  has_6m_data %>%
  filter(Intervention == "Control") %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup()

# logistic regression model
summary(
  
  glm(lv_w_in_6m ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl,
    data = logit_mod_data_con,
    family = "binomial")
  
  )
```

```{r}
# Capture one row per patient
logit_mod_data_int <- 
  has_6m_data %>%
  filter(Intervention == "Control") %>%
  group_by(Arb_PersonId) %>%
  slice_head() %>%
  ungroup()

# logistic regression model
summary(
  
  glm(lv_w_in_6m ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl,
    data = logit_mod_data_int,
    family = "binomial")
  
  )
```


# 2. define weight loss success as any weight loss of the last visit compared to the index WPV.
```{r}
wt_loss_sccs <- 
  ee %>% 
  group_by(Arb_PersonId, Intervention) %>%
  arrange(EncounterDate) %>%
  slice_tail() %>%
  ungroup() %>%
  mutate(wt_loss = ifelse(Weight_dv <= Weight_bl, 1, 0))
```


# 3. fit a logistic regression for the binary weight loss success outcomes using the subgroup of sample with the last visit after 6m
```{r}
logit_mod_wt_ls_data <- wt_loss_sccs %>%
  filter(Arb_PersonId %in% (has_6m_data %>% filter(lv_w_in_6m == 0) %>% pull(Arb_PersonId)))

summary(
  glm(wt_loss ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl,
    data = logit_mod_wt_ls_data,
    family = "binomial")
)
  
```


# 4. fit a logistic regression for the binary weight loss success outcomes using the full sample with any follow-up visit regardless the last visit is within 6m or after 6m
```{r}
summary(
  glm(wt_loss ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl,
    data = wt_loss_sccs,
    family = "binomial")
)
  
```

