---
title: "PATHWEIGH Logistic Regression Models EE-ENE"
format:
  html:
    toc: true
    embed-resources: true
    # grid:
    #   sidebar-width: 0px
    #   body-width: 2000px
    #   margin-width: 0px
    #   gutter-width: 1.5rem
      
editor: source
---


```{r}
#| echo: false
# Carlos Rodriguez PhD. CU Dept. of Family Medicine
# Control Phase Models - Development of the statistical model for the EE and 
# ENE subgroups in both control and intervention phases.
```

```{r, load packages}
#| echo: false
pacman::p_load(here,         # For managing directory paths
               magrittr,     # For the assignment pipe operator %<>%
               tidyverse,    # For data manipulation tools
               data.table,   # For reading .csv files
               openxlsx,     # For reading .xlsx files
               tictoc,       # For timing and benchmarking functions
               gtsummary,    # For tables
               DT,
               car,
               geepack,
               install = FALSE)
```


```{r}
#| echo: false

# Set the project root
proj_root <- "S:/FM/PATHWEIGH/Quantitative/Projects/"

# Set the data delivery date
delivery <- 20231010

# Load generate_plot function --------------------------------------------------
source(str_c(proj_root, "emr_data_processing/subscripts/generate_model_plots.R"))

# Load processed data ----------------------------------------------------------
load(str_c(proj_root, "dataset_", delivery, "/data/mod_data_", delivery, ".Rdata"))
```


```{r, echo = F, eval=F}
# Time invariant covariates linked to index date in each phase of the treatment
# Age_cat - could change across each intervention
mod_data %>%
  group_by(Arb_PersonId) %>%
  summarise(n = n_distinct(Age_cat)) %>%
  filter(n > 1) %>%
  nrow()

# Sex - Should not change across the intervention periods
# Should end up with 0 rows
mod_data %>%
  group_by(Arb_PersonId) %>%
  summarise(n = n_distinct(Sex)) %>%
  filter(n > 1) %>%
  nrow()

# Race - Should not change across the intervention periods
# Should end up with 0 rows
mod_data %>%
  group_by(Arb_PersonId) %>%
  summarise(n = n_distinct(Race_Ethnicity)) %>%
  filter(n > 1) %>%
  nrow()
```

# Eligible and Enrolled Patients - All records in mod_data
```{r}
#| echo: false
#| eval: true

# Counts any given individual in both intervention and control phase
mod_data %>%
  filter(EE == 1) %>%
  mutate(Race_Ethnicity = fct_na_value_to_level(Race_Ethnicity, level = "Unknown")) %>%
  select(Age, Sex, Race_Ethnicity, Intervention, Weight_bl, Weight_dv, BMI) %>%
  tbl_summary(by = Intervention,
              missing = "ifany",
              statistic = list(all_continuous() ~ c("{mean} ({sd})")),
              label = list(Race_Ethnicity ~ "Race/Ethnicity")) %>%
  add_overall() %>%
  as_flex_table() %>%
  flextable::autofit()
```

# Eligible and Enrolled Patients - One record per patient per intervention
```{r}
mod_data %>%
  filter(EE == 1) %>%
  group_by(Arb_PersonId, Intervention) %>%
  arrange(EncounterDate) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(Race_Ethnicity = fct_na_value_to_level(Race_Ethnicity, level = "Unknown")) %>%
  select(Age, Sex, Race_Ethnicity, Intervention, Weight_bl, Weight_dv, BMI) %>%
  tbl_summary(by = Intervention,
              missing = "ifany",
              statistic = list(all_continuous() ~ c("{mean} ({sd})")),
              label = list(Race_Ethnicity ~ "Race/Ethnicity")) %>%
  add_overall() %>%
  as_flex_table() %>%
  flextable::autofit()
```


# Eligible and Not Enrolled Patients - All records in mod_data
```{r}
#| echo: false
#| eval: true

# Counts any given individual in both intervention and control phase
mod_data %>%
  filter(EE == 0) %>%
  mutate(Race_Ethnicity = fct_na_value_to_level(Race_Ethnicity, level = "Unknown")) %>%
  select(Age, Sex, Race_Ethnicity, Intervention, Weight_bl, Weight_dv, BMI) %>%
  tbl_summary(by = Intervention,
              missing = "ifany",
              statistic = list(all_continuous() ~ c("{mean} ({sd})")),
              label = list(Race_Ethnicity ~ "Race/Ethnicity")) %>%
  add_overall() %>%
  as_flex_table() %>%
  flextable::autofit()
```




# Eligible and Not Enrolled - One record per patient, per intervention phase
```{r}
mod_data %>%
  filter(EE == 0) %>%
  group_by(Arb_PersonId, Intervention) %>%
  arrange(EncounterDate) %>%
  slice_head() %>%
  ungroup() %>%
  mutate(Race_Ethnicity = fct_na_value_to_level(Race_Ethnicity, level = "Unknown")) %>%
  select(Age, Sex, Race_Ethnicity, Intervention, Weight_bl, Weight_dv, BMI) %>%
  tbl_summary(by = Intervention,
              missing = "ifany",
              statistic = list(all_continuous() ~ c("{mean} ({sd})")),
              label = list(Race_Ethnicity ~ "Race/Ethnicity")) %>%
  add_overall() %>%
  as_flex_table() %>%
  flextable::autofit()

```




# Logistic Regression Models
- All coefficients are exponentiated to reflect odds ratios
Variables
- Intervention (renamed to Phase), numerical binary 
- EE, numerical binary
- Weight_dv, numeric continuous, kgs. Taken from encounter
- Age_cat, character categorical. Captured from index visit in each phase
  - Where to capture index visit in intervention phase?
- Sex, character categorical, captured from control phase index visit.
- Year_at_ind, categorical, captured at the index visit in each phase
- Weight_bl, numeric continuous, baseline weight, captured at the index visit in each phase
- N_days_post_id, numeric discrete, number of days between the encounter and the participants index visit
- N_days_post_180, numeric discrete, number of days between the encounter and the 180day/6month time point of the index visit

## Eligible & Enrolled predicted by Age, Sex, Race, Yeart at index, Baseline Weight, and Intervention phase
```{r}

# Make modifications to the names and values of the phase variables so that
# the output of the lm() summary is not so cumbersome to read
mod_data %<>%
  mutate(Phase = Intervention) %>%
  mutate(Phase = case_match(Phase, 
                        "Control" ~ 0,
                        "Intervention" ~ 1))

# Capture 1 record per patient per phase
log_data <- 
  mod_data %>%
  group_by(Arb_PersonId, Phase) %>%
  arrange(EncounterDate) %>%
  slice_head(n = 1) %>%
  ungroup()

```


```{r}
m <- glm(EE ~ Age_cat + Sex + Race_Ethnicity + Weight_bl + Phase, 
         data=log_data,
         # family = "binomial",
         family = binomial(link = "logit"),
         )

broom::tidy(m, exp = FALSE)
```


```{r, eval = F, echo=F}
# geepack geeglm() gives some really odd statistics
# Perhaps because not everyone has a cluster
m <- geeglm(EE ~ Age_cat + Sex + Race_Ethnicity + Weight_bl + Phase, 
         data=log_data,
         id = Arb_PersonId,
         # corstr = "exchangeable",
         # corstr = "independent", # gives error
         family = "binomial")

broom::tidy(m, exp = FALSE)

# How many people have an index visit in both control and intervention to cluster?
# 44,483
log_data %>%
  group_by(Arb_PersonId) %>%
  summarise(n_phase = n_distinct(Phase)) %>%
  filter(n_phase == 2) %>%
  nrow()

# Total number of distinct patients
# 214,615 total unique patients
log_data %>% distinct(Arb_PersonId)

# Percentage of patients with visits in both control and intervention phase
44483/214615 * 100
```


```{r, eval = F, echo=F}
# Capture only one record per patient
log_data2 <- 
  log_data %>%
  group_by(Arb_PersonId) %>%
  slice_head(n = 1) 

# Test what happens to the statistic values with a different data set
m <- geeglm(EE ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl + Phase, 
         data=log_data2,
         id = Arb_PersonId,
         # corstr = "exchangeable",
         # corstr = "independent", # gives error
         family = "binomial")

broom::tidy(m, exp = FALSE)
```
```{r, eval = F, echo=F}
# Test what happens to the statistic values with a different data set
m <- glm(EE ~ Age_cat + Sex + Race_Ethnicity + Year_at_ind + Weight_bl + Phase, 
         data=log_data2,
         family = "binomial")

broom::tidy(m, exp = FALSE)
```

```{r, eval = F, echo=F}
colors <- c("#440154FF","#1565c0")
mod_data %>%
mutate(EE = case_match(EE, 
                        0 ~ "ENE",
                        1 ~ "EE")) %>%
ggplot(., aes(x = EE, color = Intervention, fill = Intervention)) +
  stat_count(alpha = 0.7) +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  theme(axis.line = element_line(color = "grey70"))
```

## Interaction between Weight_bl and Phase
```{r}
m <- glm(EE ~ Age_cat + Sex + Race_Ethnicity + Weight_bl + Phase + Weight_bl * Phase, 
         data=log_data,
         family = "binomial")

broom::tidy(m, exp = FALSE)
```


<!-- ## Interaction between Year at index and Phase -->
<!-- - Model matrix is rank deficient -->
```{r, echo = FALSE}
# m <- lm(EE ~ Age_cat + Sex + Race_Ethnicity + Weight_bl + Phase + Year_at_ind*Phase, 
#          id = Arb_PersonId,
#          data=log_data,
#          family = "binomial")
# 
# broom::tidy(m, exp = FALSE)
```

```{r, echo = FALSE, eval = FALSE}
# # Get model matrix ...
# X <- model.matrix(~~ Age_cat + Sex + Race_Ethnicity + Weight_bl + Phase + Year_at_ind*Phase, data=log_data)
# 
# # Get rank of model matrix
# qr(X)$rank
# 
# # Get number of parameters of the model = number of columns of model matrix
# ncol(X)
# 
# # See if model matrix has full rank
# ncol(X) == qr(X)$rank
```

## Interaction between Race/ethnicity and Phase
```{r}
m <- glm(EE ~ Age_cat + Sex + Race_Ethnicity + Weight_bl + Phase + Race_Ethnicity*Phase, 
         data=log_data,
         family = "binomial")

broom::tidy(m, exp = FALSE)
```


## Interaction between Sex and Phase
```{r}
m <- glm(EE ~ Age_cat + Sex + Race_Ethnicity + Weight_bl + Phase + Phase * Sex, 
         data=log_data,
         family = "binomial")

broom::tidy(m, exp = FALSE)
```


## Interaction with Age
```{r}
m <- glm(EE ~ Age_cat + Sex + Race_Ethnicity + Weight_bl + Phase + Phase * Age_cat, 
         data=log_data,
         family = "binomial")

broom::tidy(m, exp = FALSE)
```


## All Interactions
```{r}
m <- glm(EE ~ Age_cat + Sex + Race_Ethnicity + Weight_bl + Phase + Phase * Age_cat + Phase * Weight_bl + Phase * Race_Ethnicity, 
         data=log_data,
         # id = Arb_PersonId,
         family = "binomial")

broom::tidy(m, exp = FALSE)
```

