---
format: docx
params:
  delivery: "20240326"
  
execute: 
  echo: false
---

```{r}
pacman::p_load(here,         # For managing directory paths
               magrittr,     # For the assignment pipe operator %<>%
               tidyverse,    # For data manipulation tools
               install = FALSE)    
```

```{r}
clinic_engagement <- read_csv("D:/PATHWEIGH//working_files/clinic_engagement.csv", col_types = cols())
```


```{r}
# Set the project root to be used as an input to the load() function
proj_root <- "D:/PATHWEIGH//"

# Set the data delivery date to the appropriate data set
delivery <- params$delivery

# Load visits post id -----------------------------------------------------------
load(str_c(proj_root, "delivery_", delivery, "/data/processed_visits_post_id_", delivery, ".Rdata"))
```


```{r}
# Drop any aberrant rows that may have been loaded, but not necessarily part
  # of the data set of interest.
  clinic_engagement %<>% 
    drop_na(DeptNameEpicId)
  
  # Update the clinic visit counts in mod_data and merge with clinic_engagement
  clinic_engagement %<>%
    select(DepartmentEpicId:Engagement)
  
  # Get the Cohort values to join in to clinic engagement for grouping
  cohort_vals <- visits_post_id %>%
    select(DepartmentEpicId, Cohort) %>%
    distinct() %>%
    filter(DepartmentEpicId %in% clinic_engagement$DepartmentEpicId)
  
  # Join cohort values
  clinic_engagement %<>%
    left_join(., cohort_vals, by = "DepartmentEpicId")
```


```{r}
# Number of clinics per cohort
cohort_n <- clinic_engagement %>%
  group_by(Cohort) %>%
  count() %>%
  mutate(Cohort_n = str_c(Cohort, ": n = ", n))

# Histogram of the engagement values
  # clinic_engagement %>%
  #   left_join(., cohort_n, by = "Cohort") %>%
  #   ggplot(., aes(Engagement)) +
  #   geom_bar() +
  #   facet_wrap(~Cohort_n) +
  #   theme_minimal() +
  #   labs(y = "Number of clinics",
  #        x = "Engagement score")
```


```{r}
# Histogram as percentages
hist <- clinic_engagement %>%
    left_join(., cohort_n, by = "Cohort") %>%
    select(Engagement, Cohort_n) %>%
    mutate(Engagement = factor(Engagement),
           Cohort = factor(Cohort_n))
```


```{r}
# 
# # This version works for counts but does not show percentages
# hist %>%
#     # group_by(Cohort)
#     ggplot(., aes(Engagement, fill = Cohort)) +
#     geom_bar(position = position_dodge2(preserve = "single"))
```


```{r, warning=FALSE, message=FALSE}
# Calculate percentage with the total number of clinics 
hist %>%
  ggplot(., aes(Engagement, fill = Cohort)) +
  geom_bar(aes(y = (..count..)/sum(..count..)),
           position = position_dodge2(preserve = "single")) +
  scale_y_continuous(labels = scales::label_percent()) +
  theme_minimal() +
  ylab("Percent of all clinics") +
  scale_fill_brewer(palette="Set2")
```
Caption: Engagement scores defined as the sum (0 -8) of a binary indicator of several measures of engagement. Measures of engagement include 1) Zoom intro meeting, 2) In-person clinic visit from a member of the PATHWEIGH team, 3) Requested support from PATHWEIGH clinical team, 4) Used PATHWEIGH e-Learning module, 5) WOF training, 6) use of PATHWEIGH Placard, 7) Attended learning community, 8) Chose practice champion.

```{r, warning=FALSE, message=FALSE}
# Calculate percentage where the denominator is total in each respective cohort
hist %>%
  group_by(Cohort, Engagement) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  ggplot(., aes(x = Engagement, y=freq, fill=Cohort)) + 
  geom_bar(stat="identity",position=position_dodge2(preserve = "single")) + 
  scale_y_continuous(labels = scales::label_percent()) +
  theme_minimal() +
  ylab("Percentage of clinics within cohort") +
  scale_fill_brewer(palette="Set2")

```
Caption: Engagement scores defined as the sum (0 -8) of a binary indicator of several measures of engagement. Measures of engagement include 1) Zoom intro meeting, 2) In-person clinic visit from a member of the PATHWEIGH team, 3) Requested support from PATHWEIGH clinical team, 4) Used PATHWEIGH e-Learning module, 5) WOF training, 6) use of PATHWEIGH Placard, 7) Attended learning community, 8) Chose practice champion.