---
title: "PATHWEIGH - Safety Officer Table"
subtitle: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
params:
  data: "20240326.RData"
---

```{r, echo = FALSE}
pacman::p_load(here,         # For managing directory paths
               tidyverse,    # For data manipulation tools
               gtsummary,
               flextable,
               install = FALSE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 7, dpi = 300)
#fig.height = 3.75
```

```{r}
#Set Start and End dates
end_date <- as.Date(lubridate::ymd(substr(params$data, 1, 8)))
start_date <- end_date-365

```


All data are captured from the time period of `r start_date` and `r end_date`.

Intervention status: Intervention status is defined by the patient's last available visit in the data set.

Vitals: Blood pressure, respiratory rate, heart rate, and temperature values were taken from the patient's last available visit.

Labs & O2CPAP/BIPAP: Lab values and were captured from the last available value within the defined time period.

Patients were considered a O2/CPAP/BIPAP user if they had a documented order within the defined time period.

Continuous measures: Percent difference is reported as the change in mean values, (Intervention mean - Control mean)/(Control mean)\*100. A difference of greater than 30% difference is considered a significant difference between the two groups (does not apply to data deliveries beyond 10/10/2023).

Count measures: Percent difference is reported as change in number of patients with evidence of O2/BPAP/BIPAP order, death, or hospitalization (does not apply to data deliveries beyond 10/10/2023).


```{r functions, echo = FALSE}
# Percent difference for continuous measures
perc_diff_continuous <- function(data, variable, by, ...) {
  vals <- t.test(data[[variable]]~as.factor(data[[by]]))$estimate
  d <- diff(vals)
  perc <- round(d/vals[1]*100,1)
  str_glue("{perc}%")
}

# Percent difference for count measures
perc_diff_count <- function(data, variable, ...){
  temp <- select(data, Intervention, all_of(variable))
  temp <- temp %>%
    group_by(Intervention) %>%
    summarise(total = n(),
              var = sum(eval(parse(text = variable)), na.rm= TRUE)) %>%
    mutate(perc = var/total * 100,
           diff = perc-lag(perc,default=first(perc)))
  val <- round(temp$diff[2],1)
  str_glue("{val}%")
}

# Count
sum_fun <- function(data, variable, ...){
  temp <- select(data, Intervention, all_of(variable))
  temp <- temp %>%
    group_by(Intervention) %>%
    summarise(total = n(),
              var = sum(eval(parse(text = variable)), na.rm= TRUE)) %>%
    mutate(perc = var/total * 1000)
  val <- round(temp$diff[2],1)
  str_glue("{val}%")
}

# Set flextable defaults for all tables
set_flextable_defaults(font.size = 10,
                       padding = 2,
                       theme_fun = "theme_vanilla",
                       table.layout="autofit")

use_df_printer()
```

```{r, echo=FALSE}
# Set the path to the emr_data_processing directory to load scripts/functions
data_delivery_date <- str_remove(params$data, ".RData")
proj_root_dir <- str_c("dataset_", data_delivery_date)
proj_parent_dir <- str_remove(here(), "emr_data_processing")
```

```{r, echo = FALSE}
# print(data_delivery_date)

# print(proj_root_dir)

# print(proj_parent_dir)
```

```{r, echo = FALSE}
# The path will be relative to emr_data_processing with here()
file_path <- str_c(proj_parent_dir, proj_root_dir, "/data/", "sot_", params$data)

# print(file_path)
```

```{r, echo = FALSE}
load(file_path)

# For Troubleshooting
# load(here("data/sot_20231010.RData"))
```


```{r, echo = FALSE}

#The `echo: false` option disables the printing of code (only output is displayed).
if (params$data == "20240326.RData"){
  t1 <- sot %>%
    select(Intervention,
           Systolic_blood_pressure:Temperature,
           A1C:eGFR,
           O2CPAPBIPAP,
           death,
           any_hosp) %>%
    mutate(Intervention = recode(Intervention,
                                 `0` = "Control (2022-03-17 to 2023-03-16)",
                                 `1` = str_c("Intervention (2023-03-17 to ", end_date, ")"))) %>%
    tbl_summary(by = Intervention,
                digits = everything() ~ 2,
                missing = "no",
                label = list(c(Systolic_blood_pressure) ~ "Systolic BP",
                             c(Diastolic_blood_pressure) ~ "Diastolic BP",
                             c(HeartRate) ~ "Heart rate",
                             c(Respiratoryrate) ~ "Respiratory rate",
                             c(O2CPAPBIPAP) ~ "O2/CPAP/BIPAP user",
                             c(death) ~ "Deaths",
                             c(any_hosp) ~ "Patients with any hospitalization"),
                type = list(c(Systolic_blood_pressure,
                           Diastolic_blood_pressure,
                           HeartRate,
                           Respiratoryrate,
                           Temperature,
                           A1C,
                           ALT,
                           AST,
                           "Cystatin C",
                           eGFR) ~ "continuous"),
                statistic = list(c(Systolic_blood_pressure,
                                   Diastolic_blood_pressure,
                                   HeartRate,
                                   Respiratoryrate,
                                   Temperature,
                                   A1C,
                                   ALT,
                                   AST,
                                   "Cystatin C",
                                   eGFR) ~ c("{mean} ({sd})"))) %>%
    add_stat(fns = list(c(Systolic_blood_pressure,
                          Diastolic_blood_pressure,
                          HeartRate,
                          Respiratoryrate,
                          Temperature,
                          A1C,
                          ALT,
                          AST,
                          "Cystatin C",
                          eGFR) ~ perc_diff_continuous,
                        c(O2CPAPBIPAP,
                          death,
                          any_hosp) ~ perc_diff_count)) %>%
    modify_header(add_stat_1 ~ "**% Diff**") %>%
    add_n() %>%
    bold_labels()
  
  
  
} else {
  t1 <- sot %>%
    select(Intervention,
           Systolic_blood_pressure:Temperature,
           A1C:eGFR,
           O2CPAPBIPAP,
           death,
           any_hosp) %>%
    mutate(Intervention = recode(Intervention,
                                 `0` = "Control",
                                 `1` = "Intervention")) %>%
    tbl_summary(by = Intervention,
                digits = everything() ~ 2,
                missing = "no",
                label = list(c(Systolic_blood_pressure) ~ "Systolic BP",
                             c(Diastolic_blood_pressure) ~ "Diastolic BP",
                             c(HeartRate) ~ "Heart rate",
                             c(Respiratoryrate) ~ "Respiratory rate",
                             c(O2CPAPBIPAP) ~ "O2/CPAP/BIPAP user",
                             c(death) ~ "Deaths",
                             c(any_hosp) ~ "Patients with any hospitalization"),
                type = list(c(Systolic_blood_pressure,
                           Diastolic_blood_pressure,
                           HeartRate,
                           Respiratoryrate,
                           Temperature,
                           A1C,
                           ALT,
                           AST,
                           "Cystatin C",
                           eGFR) ~ "continuous"),
                statistic = list(c(Systolic_blood_pressure,
                                   Diastolic_blood_pressure,
                                   HeartRate,
                                   Respiratoryrate,
                                   Temperature,
                                   A1C,
                                   ALT,
                                   AST,
                                   "Cystatin C",
                                   eGFR) ~ c("{mean} ({sd})"))) %>%
    add_stat(fns = list(c(Systolic_blood_pressure,
                          Diastolic_blood_pressure,
                          HeartRate,
                          Respiratoryrate,
                          Temperature,
                          A1C,
                          ALT,
                          AST,
                          "Cystatin C",
                          eGFR) ~ perc_diff_continuous,
                        c(O2CPAPBIPAP,
                          death,
                          any_hosp) ~ perc_diff_count)) %>%
    modify_header(add_stat_1 ~ "**% Diff**") %>%
    add_n() %>%
    bold_labels()
}
```

```{r}

# Function to calculate the average number of hospitalizations per 1,000 patients

my_stats <- function(data, ...) {
  marker_sum <- sum(data$n_hospitalizations, na.rm = TRUE)
  marker_perc <- marker_sum / dim(data)[1] * 1000
  dplyr::tibble(
    marker_sum = marker_perc
  )
}

# Test the output of my_stats

#my_stats(sot)
if (params$data == "20240326.RData"){
  t2 <-
    sot %>%
    select(n_hospitalizations) %>%
    tbl_custom_summary(stat_fns = list(c(n_hospitalizations) ~ my_stats),
                       statistic = list(c(n_hospitalizations) ~ "{marker_sum}"),
                       label = list(n_hospitalizations ~ "Average number of days hospitalized per 1000 patients")) %>%
    # add_stat(fns = list(c(n_hospitalizations) ~ perc_diff_continuous)) %>%
    # modify_header(add_stat_1 ~ "**% Diff**") %>%
    add_n() %>%
    bold_labels()
  
  }else{
    
  t2 <-
    sot %>%
    select(Intervention,
           n_hospitalizations) %>%
    mutate(Intervention = recode(Intervention,
                                 `0` = "Control",
                                 `1` = "Intervention")) %>%
    tbl_custom_summary(by = Intervention,
                       stat_fns = list(c(n_hospitalizations) ~ my_stats),
                       statistic = list(c(n_hospitalizations) ~ "{marker_sum}"),
                       label = list(n_hospitalizations ~ "Average number of days hospitalized per 1000 patients")) %>%
    add_stat(fns = list(c(n_hospitalizations) ~ perc_diff_continuous)) %>%
    modify_header(add_stat_1 ~ "**% Diff**") %>%
    add_n() %>%
    bold_labels()
  }
```

```{r}
# Stack tables
tbl_stack(list(t1, t2))
```

