---
title: "AOMs & Procedures by Year"
format: 
  docx:
    reference-doc: "D:/PATHWEIGH/custom-reference-doc.docx"

execute: 
  echo: false
---

```{r}
 # Load pp_data to get the patients in Aim1A

# load the visits post_id data to get the index visit rows that contain procedures and AOMs

# Review how AOMs and Procedures are captured
# Bariatric Surgery - At any time during the phase
# - 10/24/2024 Stats group, capture the medications that were started in agiven phase even if they 
# were carried over from control to intervention
# If the reference visits are from the Control phase, then keep records
# where the OrderedDate is before the cross over date. This will capture
# records of AOMs that were ordered. n.b. OrderDate doesn't always equal
# the start date

# If the reference visits are from the Intervention phase, then keep the
# records where 1) the OrderedDate is on or after the cross over date to
# get records for those that were ordered an AOM in intervention; 2) the
# EndDate is on or after the cross over date to get records for those that
# had an Ordered date before the cross over, but continued medication into
# the intervention; and 3) the EndDate is missing, to get records for those
# that are continuing AOM medication
# This will count those that had an order in intervention and/or had
# continued use from the control
```

```{r}
pacman::p_load(tidyverse, 
               gtable,
               install = FALSE)

library(magrittr, include = "%<>%")
```

```{r}
# Load the pp_data - Contains all visits after the index date from patients
# with 2 or more visits in both control and intervention phase
load("D:/PATHWEIGH/delivery_20240917/data/pp_data_20240917.RData")
```

```{r}
# Load visits_post_id, all visits on or after the index date for EE patients
load("D:/PATHWEIGH/delivery_20240917/data/visits_post_id_20240917.RData")
```

```{r}
# Get the encounter ids for all of the index visits in pp_data
index_ids <-
    pp_data %>%
    filter(IndexVisit == 1) %>%
    select(Arb_EncounterId)
```

```{r}
# Filter the index_ids from visits_post_id
visits_post_id %<>%
  filter(Arb_EncounterId %in% index_ids$Arb_EncounterId)
```

# Overall total number of ordered AOMs in each phase
```{r}
visits_post_id %>%
  group_by(Intervention.factor) %>%
  summarise(total_n_aom = sum(N_Meds_AOM)) %>%
  knitr::kable()
```

# Overall total number of ordered AOMs in each year
```{r}
visits_post_id %>%
  group_by(Year) %>%
  summarise(total_n_aom = sum(N_Meds_AOM)) %>%
  knitr::kable()
```

# Number of ordered AOMs in each year by intervention
```{r}
visits_post_id %>%
  group_by(Year, Intervention.factor) %>%
  summarise(total_n_aom = sum(N_Meds_AOM)) %>%
  knitr::kable()
```

# Number of patients with at least one ordered AOM by phase
```{r}
visits_post_id %>%
  mutate(aom = ifelse(N_Meds_AOM > 0, 1, 0)) %>%
  group_by(Intervention.factor) %>%
  summarise(total_n_pts_w_aom = sum(aom)) %>%
  ungroup() %>%
  mutate(percent_N = round(total_n_pts_w_aom / 9358 * 100, 2)) %>%
  knitr::kable()
```

# Overall total number of patients with at least one ordered AOM in each year
```{r}
left_join(
  (visits_post_id %>%
  mutate(aom = ifelse(N_Meds_AOM > 0, 1, 0)) %>%
  group_by(Year) %>%
  summarise(total_n_pts_w_aom = sum(aom)) %>%
  ungroup()),

  (visits_post_id %>%
  filter(IndexVisit == 1) %>%
  group_by(Year) %>%
  count() %>%
  ungroup()),
  
  by = "Year"
) %>%
mutate(percent_n =  round(total_n_pts_w_aom / n * 100, 2)) %>%
knitr::kable()
```

# Number of patients with at least one ordered AOM in each year by intervention
```{r}
left_join(
  (visits_post_id %>%
  mutate(aom = ifelse(N_Meds_AOM > 0, 1, 0)) %>%
  group_by(Year, Intervention.factor) %>%
  summarise(total_n_pts_w_aom = sum(N_Meds_AOM)) %>%
  ungroup()),

  (visits_post_id %>%
  filter(IndexVisit == 1) %>%
  group_by(Year, Intervention.factor) %>%
  count() %>%
  ungroup()),

  by = c("Year", "Intervention.factor")
) %>%
mutate(percent_n =  round(total_n_pts_w_aom / n * 100, 2)) %>%
knitr::kable()

```


# Overall total number of bariatric procedures in each phase
```{r}
visits_post_id %>%
  group_by(Intervention.factor) %>%
  summarise(total_n_procs = sum(BariatricSurgery)) %>%
  ungroup() %>%
  mutate(percent_N = round(total_n_procs / 9358 * 100, 2)) %>%
  knitr::kable()
```

# Overall total number of bariatric procedures in each year
```{r}
left_join(
  (visits_post_id %>%
  group_by(Year) %>%
  summarise(total_n_procs = sum(BariatricSurgery)) %>%
  ungroup()),

  (visits_post_id %>%
  filter(IndexVisit == 1) %>%
  group_by(Year) %>%
  count() %>%
  ungroup()),

  by = "Year"
) %>%
mutate(percent_n = round(total_n_procs / n * 100, 2)) %>%
knitr::kable()
```

# Number of bariatric procedures in each year by intervention
```{r}
left_join(
  (visits_post_id %>%
  group_by(Year, Intervention.factor) %>%
  summarise(total_n_procs = sum(BariatricSurgery)) %>%
  ungroup()),

  (visits_post_id %>%
  filter(IndexVisit == 1) %>%
  group_by(Year, Intervention.factor) %>%
  count() %>%
  ungroup()),

  by = c("Year", "Intervention.factor")
) %>%
mutate(percent_n = round(total_n_procs / n * 100, 2)) %>%
knitr::kable()
```